---
title: "Co-Occurence Network"
output: html_document
---

This code was used to generate the PS network, as well as various networks using shifting cutoffs. This code takes a while, so various parts are commented out and just used as examples.

###Original Co-Occur Network
```{r session}
rm(list = ls())
if (is.integer(dev.list())){dev.off()}
cat("\014")
set.seed(1)
source("functions.R")
sessionInfo()
```

```{r loading_data}
library(parallel) ## used for parallel processing - to speed up the loop
##### Fisher's exact edges code

###Essentially the tests for gene fisher tests for all gene comparisons.

avana_res <- read.delim("Data/avana_output_v2.txt") %>% dplyr::select(-c(MEAN_FC_Shuffle_Mean,SD_Shuffle_Mean,MEAN_FC,n,n_above,percentage,geneScores,GENE_Exp,Exp,Mean_FC_Z_Score,ranking))

temp_hits <- avana_res %>% filter(hit == 1) %>% droplevels()
temp_avana <- avana_res %>% filter(GENE %in% temp_hits$GENE)
tab <- table(temp_hits$GENE)
tab <- tab[tab>1]
g1 = c()
g2 = c()
fish_p = c()
count = c()

temp_tab <- tab
```

Generating the network of the actual cutoff
```{r original_network}
for (i in 1:length(tab)){
  print(i)
  GENE1 = names(tab)[i]
  temp_tab <- temp_tab[names(temp_tab) != GENE1]
  temp_p <- mclapply(X = as.array(names(temp_tab)),FUN = function(X) fisher_edges(GENE1 = GENE1,GENE2 = X,data_feed = temp_avana), mc.cores = 15)
  count = c(count,(temp_tab + tab[i]))
  g1 = c(g1,rep(GENE1, length(temp_tab)))
  g2 = c(g2,as.array(names(temp_tab)))
  fish_p = c(fish_p, unlist(temp_p))
}

fisher_results <- data.frame(g1,g2,fish_p,count)
#write_delim(fisher_results,"Data/fisher_edges_tsg_v2_2_05.txt",delim = "\t")

###Using a FDR cutoff of 0.01 
fisher_results$fish_FDR = p.adjust(fisher_results$fish_p,method = "fdr")
fisher_results_fil <- fisher_results %>% filter(fish_FDR < 0.01)
#write_delim(fisher_results_fil,"Data/fisher_results_res_fdr_0.01_2_7_20.txt",delim = "\t")
```

This code chunk evaluates the percentage of the network observed in Human Net.
```{r orig_net_humannet}
HumanNet.FN <- read.delim("Data/HumanNet-FN.tsv", header = FALSE)
colnames(HumanNet.FN) = c("GENE1", "GENE2", "FN_Score")

fisher_results_HuNet <- fisher_results_fil

V1 <- as.vector(as.character(fisher_results_HuNet$g1)) #%>% unique()
entrez_IDS <- mapIds(org.Hs.eg.db, V1, 'ENTREZID', 'SYMBOL')
fisher_results_HuNet$GENE1_entrez_ID = entrez_IDS

V2 <- as.vector(as.character(fisher_results_HuNet$g2)) #%>% unique()
entrez_IDS <- mapIds(org.Hs.eg.db, V2, 'ENTREZID', 'SYMBOL')
fisher_results_HuNet$GENE2_entrez_ID = entrez_IDS
fisher_results_HuNet$Hunet = 0

V1 <- as.vector(as.character(fisher_results$g1)) #%>% unique()
entrez_IDS <- mapIds(org.Hs.eg.db, V1, 'ENTREZID', 'SYMBOL')
fisher_results$GENE1_entrez_ID = entrez_IDS

V2 <- as.vector(as.character(fisher_results$g2)) #%>% unique()
entrez_IDS <- mapIds(org.Hs.eg.db, V2, 'ENTREZID', 'SYMBOL')
fisher_results$GENE2_entrez_ID = entrez_IDS
fisher_results$Hunet = 0
hunetgenes <- c(HumanNet.FN$GENE1, HumanNet.FN$GENE2) %>% unique()

rm(V1, V2, entrez_IDS)

fisher_results <-  fisher_results %>% filter(GENE1_entrez_ID %in% hunetgenes) %>% filter(GENE2_entrez_ID %in% hunetgenes)
fisher_results_HuNet <- fisher_results_HuNet %>% filter(GENE1_entrez_ID %in% hunetgenes) %>% filter(GENE2_entrez_ID %in% hunetgenes)
fisher_results_fil <- fisher_results %>% filter(g1 == "")

genes <-
  unique(c(
    as.character(fisher_results$g1),
    as.character(fisher_results$g2)
  ))
gene_entrez <-
  unique(c(
    as.character(fisher_results$GENE1_entrez_ID),
    as.character(fisher_results$GENE2_entrez_ID)
  ))
HumanNet.FN <-
  HumanNet.FN %>% filter(GENE1 %in% gene_entrez) %>% filter(GENE2 %in% gene_entrez)

###Checking resulting network human net overlap
for (i in 1:nrow(fisher_results_HuNet)) {
  #print(i)
  GENE1_entrez = fisher_results_HuNet[i, "GENE1_entrez_ID"]
  GENE2_entrez = fisher_results_HuNet[i, "GENE2_entrez_ID"]
  temp_hunet <-
    HumanNet.FN %>% filter(GENE1 == GENE1_entrez) %>% filter(GENE2 == GENE2_entrez)
  if (nrow(temp_hunet) != 0) {
    fisher_results_HuNet[i, "Hunet"] = 1
  }
  temp_hunet2 <-
    HumanNet.FN %>% filter(GENE1 == GENE2_entrez) %>% filter(GENE2 == GENE1_entrez)
  if (nrow(temp_hunet2) != 0) {
    fisher_results_HuNet[i, "Hunet"] = 1
  }
}

```

###Testing Cutoffs
This next code chunk is used to combine the previous two code chunks and evaluate at different cutoffs (used for supplemental figure 4b). This code takes a little while to run, so it is commented out and only shows an example of one interation.
```{r testing_cutoffs}
real_sum_edges <- sum(fisher_results_HuNet$Hunet) / nrow(fisher_results_HuNet)
num_genes_avail <- c(length(tab))
gene_network <- c(length(unique(c(fisher_results_HuNet$g1,fisher_results_HuNet$g2))))
interval_Z <- c(min(temp_hits$Mod_Z_Score))
percent_edges <- c(real_sum_edges)
#interval_seq <- seq(3.5, 8, 0.25)
interval_seq <- c(6.5) ###choosing a later data point

rm(fisher_results,HumanNet.FN,fisher_results_fil,fisher_results_HuNet,temp_avana,temp_hits,temp_hunet,temp_hunet2,g1,g2,gene_entrez,hunetgenes,genes)

for (interval in interval_seq){
  #browser()
  print(interval)
  temp_hits <- avana_res %>% filter(Mod_Z_Score > interval) %>% droplevels()
  temp_avana <- avana_res %>% filter(GENE %in% temp_hits$GENE)
  temp_avana$hit = 0
  temp_avana$hit[temp_avana$Mod_Z_Score > interval] = 1
  
  tab <- table(temp_hits$GENE)
  tab <- tab[tab>1]
  
  g1 = c()
  g2 = c()
  fish_p = c()
  count = c()
  
  temp_tab <- tab
  num_genes_avail <- c(num_genes_avail,length(tab))
  
  for (i in 1:length(tab)){
    print(i)
    GENE1 = names(tab)[i]
    temp_tab <- temp_tab[names(temp_tab) != GENE1]
    temp_p <- mclapply(X = as.array(names(temp_tab)),FUN = function(X) fisher_edges(GENE1 = GENE1,GENE2 = X,data_feed = temp_avana), mc.cores = 20)
    count = c(count,(temp_tab + tab[i]))
    g1 = c(g1,rep(GENE1, length(temp_tab)))
    g2 = c(g2,as.array(names(temp_tab)))
    fish_p = c(fish_p, unlist(temp_p))

  }
  fisher_results <- data.frame(g1,g2,fish_p,count)
  
  fisher_results_fil <- fisher_results
  
  fisher_results_fil$fish_FDR = p.adjust(fisher_results_fil$fish_p,method = "fdr")
  
  fisher_results_fil <- fisher_results_fil %>% filter(fish_FDR < 0.01)
  
  HumanNet.FN <- read.delim("Data/HumanNet-FN.tsv", header = FALSE)
  colnames(HumanNet.FN) = c("GENE1", "GENE2", "FN_Score")
  
  ###Human Net files, FN is Human net without coessential network.
  
  fisher_results_HuNet <- fisher_results_fil
  
  V1 <- as.vector(as.character(fisher_results_HuNet$g1)) #%>% unique()
  entrez_IDS <- mapIds(org.Hs.eg.db, V1, 'ENTREZID', 'SYMBOL')
  fisher_results_HuNet$GENE1_entrez_ID = entrez_IDS
  
  V2 <- as.vector(as.character(fisher_results_HuNet$g2)) #%>% unique()
  entrez_IDS <- mapIds(org.Hs.eg.db, V2, 'ENTREZID', 'SYMBOL')
  fisher_results_HuNet$GENE2_entrez_ID = entrez_IDS
  fisher_results_HuNet$Hunet = 0
  
  V1 <- as.vector(as.character(fisher_results$g1)) #%>% unique()
  entrez_IDS <- mapIds(org.Hs.eg.db, V1, 'ENTREZID', 'SYMBOL')
  fisher_results$GENE1_entrez_ID = entrez_IDS
  
  V2 <- as.vector(as.character(fisher_results$g2)) #%>% unique()
  entrez_IDS <- mapIds(org.Hs.eg.db, V2, 'ENTREZID', 'SYMBOL')
  fisher_results$GENE2_entrez_ID = entrez_IDS
  fisher_results$Hunet = 0
  hunetgenes <- c(HumanNet.FN$GENE1, HumanNet.FN$GENE2) %>% unique()
  
  rm(V1, V2, entrez_IDS)
  
  ###Identifying genes within human net
  
  fisher_results <-  fisher_results %>% filter(GENE1_entrez_ID %in% hunetgenes) %>% filter(GENE2_entrez_ID %in% hunetgenes)
  fisher_results_HuNet <- fisher_results_HuNet %>% filter(GENE1_entrez_ID %in% hunetgenes) %>% filter(GENE2_entrez_ID %in% hunetgenes)
  fisher_results_fil <- fisher_results %>% filter(g1 == "")
  
  genes <-
    unique(c(
      as.character(fisher_results$g1),
      as.character(fisher_results$g2)
    ))
  gene_entrez <-
    unique(c(
      as.character(fisher_results$GENE1_entrez_ID),
      as.character(fisher_results$GENE2_entrez_ID)
    ))
  HumanNet.FN <-
    HumanNet.FN %>% filter(GENE1 %in% gene_entrez) %>% filter(GENE2 %in% gene_entrez)
  
  ###Checking resulting network human net overlap
  for (i in 1:nrow(fisher_results_HuNet)) {
    #print(i)
    GENE1_entrez = fisher_results_HuNet[i, "GENE1_entrez_ID"]
    GENE2_entrez = fisher_results_HuNet[i, "GENE2_entrez_ID"]
    temp_hunet <-
      HumanNet.FN %>% filter(GENE1 == GENE1_entrez) %>% filter(GENE2 == GENE2_entrez)
    if (nrow(temp_hunet) != 0) {
      fisher_results_HuNet[i, "Hunet"] = 1
    }
    temp_hunet2 <-
      HumanNet.FN %>% filter(GENE1 == GENE2_entrez) %>% filter(GENE2 == GENE1_entrez)
    if (nrow(temp_hunet2) != 0) {
      fisher_results_HuNet[i, "Hunet"] = 1
    }
  }
  interval_Z <- c(interval_Z,interval)
  gene_network <- c(gene_network,length(unique(c(fisher_results_HuNet$g1,fisher_results_HuNet$g2))))
  sum_edges <- sum(fisher_results_HuNet$Hunet) / nrow(fisher_results_HuNet)
  percent_edges <- c(percent_edges,sum_edges)
  rm(fisher_results,HumanNet.FN,fisher_results_fil,fisher_results_HuNet,temp,temp_avana,temp_hits,temp_hunet,temp_hunet2,g1,g2,gene_entrez,hunetgenes,genes)
}   
#result_df<- data.frame(interval_Z,num_genes_avail,percent_edges,gene_network)
#write_delim(result_df,"Data/Human_net_cutoff_results.txt",delim = "\t")


```
