---
title: "Fold-Change Calculation Shuffle Correction"
output:
  html_document:
    df_print: paged
---

The following code was used to generate shuffled fold-change distributions in order to calculate modified z-scores. Each code chunk starts with a different data set used with a different library (Wang AML screens, Sanger DepMap, and Avana DepMap). Code chunks vary with data manipulation, however bootstrapping loops remain relatively constant. Each code chunk starts from calculated fold-change data (CRISPRCleanR corrected for Avana and Sanger DepMap data sets, FCs directly from Wang raw reads).


##R Session
Not all libraries were used for each code chunk. 

```{r session}
rm(list = ls())
if (is.integer(dev.list())) {
  dev.off()
}
cat("\014")
source("./functions.R")
set.seed(1)
sessionInfo()

```

##Avana Data

``` {r Avana}
rm(list = ls())
if (is.integer(dev.list())) {
  dev.off()
}
cat("\014")
source("./functions.R")
set.seed(1)

### Post crisprcleanr fold-change data

fold_dat <-
  read_delim(
    "Data/Avana_FC_Comb_FC_Corrected",
    "\t",
    escape_double = FALSE,
    trim_ws = TRUE
  )

head(fold_dat)

### Loading in replicate map

replicate_map <-
  read_delim(
    "Data/replicate_map.csv",
    ",",
    escape_double = FALSE,
    trim_ws = TRUE
  )

head(replicate_map)

replicate_map <- replicate_map %>% dplyr::select(-pDNA_batch)

fold_dat <- gather(fold_dat, replicate_ID, FC, -c(X1, GENE))

replicate_map_change <- replicate_map

### Manipulating replicate map to be consistent

replicate_map_change$replicate_ID <-
  gsub(' ', '_', replicate_map_change$replicate_ID)

replicate_map_change$replicate_ID <-
  gsub('/', '_', replicate_map_change$replicate_ID)

replicate_map_change$replicate_ID <-
  gsub(',', '_', replicate_map_change$replicate_ID)

### Some replicates didn't match up perfectly, needed to isolate those and handle them independently

fold_dat_found <-
  fold_dat %>% filter(replicate_ID %in% replicate_map$replicate_ID)

fold_dat_miss <-
  fold_dat %>% filter(replicate_ID %!in% replicate_map$replicate_ID)

unique(fold_dat_miss$replicate_ID[fold_dat_miss$replicate_ID %!in% replicate_map_change$replicate_ID])

fold_dat_found <-
  left_join(fold_dat_found, replicate_map, by = "replicate_ID")

fold_dat_miss <-
  left_join(fold_dat_miss, replicate_map_change, by = "replicate_ID")

fold_dat <- rbind(fold_dat_found, fold_dat_miss)

fold_dat_sd_cell <-
  data.frame(Cell_Line = character(0), SD_Shuffle = numeric(0))

fold_dat_mean_cell <-
  data.frame(Cell_Line = character(0), MEAN_FC_Shuffle = numeric(0))

length(unique(fold_dat$DepMap_ID)) #563

temp <- fold_dat

### Adding the entrez IDs for bulk of analysis. 

V1 <- as.vector(as.character(temp$GENE))

entrez_IDS <- mapIds(org.Hs.eg.db, V1, 'ENTREZID', 'SYMBOL')

temp$entrez_ID <- entrez_IDS

rm(
  entrez_IDS,
  V1,
  temp,
  fold_dat_found,
  fold_dat_miss,
  replicate_map_change,
  replicate_map
)

### Calculating null distribution mean and sd for modified z-score. run 1000 times, only 1 time here for example purposes

for (cell in unique(fold_dat$DepMap_ID)) {
  print(cell)
  fold_dat_shuffle <- fold_dat %>% filter(DepMap_ID == cell)
  #  for (i in 1:1000) {
  for (i in 1) {
    print(i)
    temp <- fold_dat_shuffle
    temp$FC <- ave(temp$FC, temp$DepMap_ID, FUN = sample)
    fold_dat_shuffle_agg <-
      aggregate(
        temp$FC,
        by = list(temp$GENE, temp$DepMap_ID),
        FUN = mean,
        na.rm = TRUE
      )
    fold_dat_shuffle_mean_cell <-
      aggregate(
        fold_dat_shuffle_agg$x,
        by = list(fold_dat_shuffle_agg$Group.2),
        FUN = mean,
        na.rm = TRUE
      )
    fold_dat_shuffle_sd_cell <-
      aggregate(
        fold_dat_shuffle_agg$x,
        by = list(fold_dat_shuffle_agg$Group.2),
        FUN = sd,
        na.rm = TRUE
      )
    colnames(fold_dat_shuffle_sd_cell) <-
      c("Cell_Line", "SD_Shuffle")
    colnames(fold_dat_shuffle_mean_cell) <-
      c("Cell_Line", "MEAN_FC_Shuffle")
    fold_dat_sd_cell <-
      rbind(fold_dat_sd_cell, fold_dat_shuffle_sd_cell)
    fold_dat_mean_cell <-
      rbind(fold_dat_mean_cell, fold_dat_shuffle_mean_cell)
  }
}

#write_delim(fold_dat_mean_cell,"Data/fold_dat_shuffle_meanFC_Avana.txt",delim = "\t")

#write_delim(fold_dat_sd_cell,"Data/fold_dat_shuffle_sdFC_Avana.txt",delim = "\t")

### Not writing files since it was a single simulation. Loading in original shuffled mean and sds 

fold_dat_mean_cell <-
  read.delim("Data/fold_dat_shuffle_meanFC_Avana.txt")

head(fold_dat_mean_cell)

fold_dat_sd_cell <-
  read.delim("Data/fold_dat_shuffle_sdFC_Avana.txt")

head(fold_dat_sd_cell)

### Aggregating these values and adding various other metrics in addition (once considered for to identify proliferation suppressor phenotype)

fold_dat_sd_cell_temp <- fold_dat_sd_cell

fold_dat_sd_cell_temp <-
  aggregate(
    fold_dat_sd_cell_temp$SD_Shuffle,
    by = list(fold_dat_sd_cell_temp$Cell_Line),
    FUN = mean,
    na.rm = TRUE
  )

colnames(fold_dat_sd_cell_temp) <- c("Cell_Line", "SD_Shuffle_Mean")

fold_dat_mean_cell_temp <- fold_dat_mean_cell

fold_dat_mean_cell_temp <-
  aggregate(
    fold_dat_mean_cell_temp$MEAN_FC_Shuffle,
    by = list(fold_dat_mean_cell_temp$Cell_Line),
    FUN = mean,
    na.rm = TRUE
  )

colnames(fold_dat_mean_cell_temp) <-
  c("Cell_Line", "MEAN_FC_Shuffle_Mean")

fold_dat_mean <-
  aggregate(
    fold_dat$FC,
    by = list(fold_dat$GENE, fold_dat$DepMap_ID),
    FUN = mean,
    na.rm = TRUE
  )

colnames(fold_dat_mean)  <- c("GENE", "Cell_Line", "MEAN_FC")

fold_dat_results <- merge(fold_dat_mean, fold_dat_mean_cell_temp)

fold_dat_results <- merge(fold_dat_results, fold_dat_sd_cell_temp)

fold_dat_count <- fold_dat %>% dplyr::count(GENE, DepMap_ID)

temp <- fold_dat %>% filter(FC > 0)

fold_dat_count_above <- temp %>% dplyr::count(GENE, DepMap_ID)

colnames(fold_dat_count_above) <- c("GENE", "Cell_Line", "n_above")

colnames(fold_dat_count) <- c("GENE", "Cell_Line", "n")

fold_dat_count <-
  merge(fold_dat_count, fold_dat_count_above, all.x = TRUE)

fold_dat_count$n_above[is.na(fold_dat_count$n_above)] <- 0

rm(fold_dat_count_above, temp)

colnames(fold_dat_count)[2] <- "Cell_Line"

### Looking at positive number of guides, something we considered to identify the phenotype at one point. 

fold_dat_count$percentage <- fold_dat_count$n_above / fold_dat_count$n

fold_dat_results <-
  merge(fold_dat_results, fold_dat_count, all.x = TRUE)

fold_dat_results$percentage <- round(fold_dat_results$percentage, digits = 5)

fold_dat_results$MEAN_FC <- round(fold_dat_results$MEAN_FC, digits = 6)

fold_dat_results$MEAN_FC_Shuffle_Mean <- round(fold_dat_results$MEAN_FC_Shuffle_Mean, digits = 6)

fold_dat_results$SD_Shuffle_Mean <- round(fold_dat_results$SD_Shuffle_Mean, digits = 6)

# write_delim(fold_dat_results, "Data/Avana_Shuffle_Corrected_FC.txt", delim = "\t")

head(fold_dat_results)
```

##Sanger Data:

```{r sanger}
rm(list = ls())
if (is.integer(dev.list())) {
  dev.off()
}
cat("\014")
source("./functions.R")
set.seed(1)

##loading in fold change data

fold_dat <-
  read_delim(
    "Data/Sanger_FC_Comb_FC_Corrected",
    "\t",
    escape_double = FALSE,
    trim_ws = TRUE
  )

head(fold_dat)

sanger_meta <- read.delim("Data/sanger_meta.txt")

head(sanger_meta)

### Gathering data to be long tables

fold_dat <- gather(fold_dat, replicate_ID, FC, -c(GENE, X1))

reps <- fold_dat %>% dplyr::select(replicate_ID) %>% unique()

### Matching the screen names to their corresponding replicates

reps$match <- 0

for (i in unique(reps$replicate_ID)) {
  find <- grep(i, sanger_meta$Experiment_Identifier)
  if (length(find) > 0) {
    reps$match[reps$replicate_ID == i] <- as.character(sanger_meta$Cell_Line[find])
  }
}

reps <- reps %>% filter(match != 0) %>% unique()

fold_dat <- fold_dat %>% filter(replicate_ID %in% reps$replicate_ID)

fold_dat <- right_join(fold_dat, reps, by = "replicate_ID")

fold_dat$FC <- round(fold_dat$FC, 6)

fold_dat <-
  fold_dat %>% filter(!is.na(FC)) %>% filter(!is.na(match)) %>% filter(!is.na(GENE))

### Demonstrating strategy on one specific cell line.

fold_dat_temp <- fold_dat %>% filter(match == "SIDM00499")

fold_dat_temp_shuffle <- fold_dat_temp

fold_dat_temp_shuffle$FC <-
  ave(fold_dat_temp_shuffle$FC, fold_dat_temp_shuffle$match, FUN = sample)

fold_dat_temp_shuffle <-
  aggregate(
    fold_dat_temp_shuffle$FC,
    by = list(fold_dat_temp_shuffle$GENE, fold_dat_temp_shuffle$match),
    FUN = mean,
    na.rm = TRUE
  )

fold_dat_temp <-
  aggregate(
    fold_dat_temp$FC,
    by = list(fold_dat_temp$GENE, fold_dat_temp$match),
    FUN = mean,
    na.rm = TRUE
  )

### Demonstrating Strategy

rm(fold_dat_temp, fold_dat_temp_shuffle)

fold_dat_sd_cell <-
  data.frame(Cell_Line = character(0), SD_Shuffle = numeric(0))

fold_dat_mean_cell <-
  data.frame(Cell_Line = character(0), MEAN_FC_Shuffle = numeric(0))

###Shuffling guides and calculating null distribution 1000 times, only calculating once for demonstration purposes.

for (cell in unique(fold_dat$match)) {
  print(cell)
  fold_dat_shuffle <- fold_dat %>% filter(match == cell)
  #  for (i in 1:1000) {
  for (i in 1) {
    print(i)
    temp <- fold_dat_shuffle
    temp$FC <- ave(temp$FC, temp$match, FUN = sample)
    fold_dat_shuffle_agg <-
      aggregate(
        temp$FC,
        by = list(temp$GENE, temp$match),
        FUN = mean,
        na.rm = TRUE
      )
    fold_dat_shuffle_mean_cell <-
      aggregate(
        fold_dat_shuffle_agg$x,
        by = list(fold_dat_shuffle_agg$Group.2),
        FUN = mean,
        na.rm = TRUE
      )
    fold_dat_shuffle_sd_cell <-
      aggregate(
        fold_dat_shuffle_agg$x,
        by = list(fold_dat_shuffle_agg$Group.2),
        FUN = sd,
        na.rm = TRUE
      )
    colnames(fold_dat_shuffle_sd_cell) <-
      c("Cell_Line", "SD_Shuffle")
    colnames(fold_dat_shuffle_mean_cell) <-
      c("Cell_Line", "MEAN_FC_Shuffle")
    fold_dat_sd_cell <-
      rbind(fold_dat_sd_cell, fold_dat_shuffle_sd_cell)
    fold_dat_mean_cell <-
      rbind(fold_dat_mean_cell, fold_dat_shuffle_mean_cell)
  }
}

###Write files commented out to avoid over writing 

#write_delim(fold_dat_mean_cell,"./fold_dat_shuffle_meanFC_Sanger.txt",delim = "\t")
#write_delim(fold_dat_sd_cell,"./fold_dat_shuffle_sdFC_Sanger.txt",delim = "\t")

###Load in the original 1000 iterations.

fold_dat_mean_cell <-
  read.delim("Data/fold_dat_shuffle_meanFC_Sanger.txt")

fold_dat_sd_cell <-
  read.delim("Data/fold_dat_shuffle_sdFC_Sanger.txt")

head(fold_dat_mean_cell)

head(fold_dat_sd_cell)


fold_dat_sd_cell_temp <- fold_dat_sd_cell

fold_dat_sd_cell_temp <-
  aggregate(
    fold_dat_sd_cell_temp$SD_Shuffle,
    by = list(fold_dat_sd_cell_temp$Cell_Line),
    FUN = mean,
    na.rm = TRUE
  )

colnames(fold_dat_sd_cell_temp) <- c("Cell_Line", "SD_Shuffle_Mean")

###Aggregating the simulations as well as the raw mean fold change values. 

fold_dat_mean_cell_temp <- fold_dat_mean_cell

fold_dat_mean_cell_temp <-
  aggregate(
    fold_dat_mean_cell_temp$MEAN_FC_Shuffle,
    by = list(fold_dat_mean_cell_temp$Cell_Line),
    FUN = mean,
    na.rm = TRUE
  )

colnames(fold_dat_mean_cell_temp) <-
  c("Cell_Line", "MEAN_FC_Shuffle_Mean")

fold_dat_mean <-
  aggregate(
    fold_dat$FC,
    by = list(fold_dat$GENE, fold_dat$match),
    FUN = mean,
    na.rm = TRUE
  )

colnames(fold_dat_mean)  <- c("GENE", "Cell_Line", "MEAN_FC")

fold_dat_results <- merge(fold_dat_mean, fold_dat_mean_cell_temp)

fold_dat_results <- merge(fold_dat_results, fold_dat_sd_cell_temp)

### At one point we also were considering the percentage of guides with positive FC as a methodology

fold_dat_count <- fold_dat %>% dplyr::count(GENE, match)

temp <- fold_dat %>% filter(FC > 0)

fold_dat_count_above <- temp %>% dplyr::count(GENE, match)

colnames(fold_dat_count_above) <- c("GENE", "match", "n_above")

fold_dat_count <-
  merge(fold_dat_count, fold_dat_count_above, all.x = TRUE)

fold_dat_count$n_above[is.na(fold_dat_count$n_above)] <- 0

rm(fold_dat_count_above, temp)

colnames(fold_dat_count)[2] <- "Cell_Line"

fold_dat_count$percentage <- fold_dat_count$n_above / fold_dat_count$n

fold_dat_results <-
  merge(fold_dat_results, fold_dat_count, all.x = TRUE)

fold_dat_results$percentage <- round(fold_dat_results$percentage, digits = 5)

#write_delim(fold_dat_results, "Sanger_Shuffle_Corrected_FC.txt", delim = "\t")

head(fold_dat_results)
```

##Wang Data:

```{r Wang}

rm(list = ls())
if (is.integer(dev.list())) {
  dev.off()
}
cat("\014")
source("./functions.R")
set.seed(1)
 
Wang_FC_combine <-
  read.delim("Data/Wang_FC_combine.txt")

#this data was already combined from previous efforts

head(Wang_FC_combine)

fold_dat_sd_cell <-
  data.frame(Cell_Line = character(0), SD_Shuffle = numeric(0))

fold_dat_mean_cell <-
  data.frame(Cell_Line = character(0), MEAN_FC_Shuffle = numeric(0))

for (cell in unique(Wang_FC_combine$Type)) {
  print(cell)
  fold_dat_shuffle <- Wang_FC_combine %>% filter(Type == cell)
  #  for (i in 1:1000) {
  for (i in 1) {
    print(i)
    temp <- fold_dat_shuffle
    temp$FC <- ave(temp$FC, temp$Type, FUN = sample)
    fold_dat_shuffle_agg <-
      aggregate(
        temp$FC,
        by = list(temp$GENE, temp$Type),
        FUN = mean,
        na.rm = TRUE
      )
    fold_dat_shuffle_mean_cell <-
      aggregate(
        fold_dat_shuffle_agg$x,
        by = list(fold_dat_shuffle_agg$Group.2),
        FUN = mean,
        na.rm = TRUE
      )
    fold_dat_shuffle_sd_cell <-
      aggregate(
        fold_dat_shuffle_agg$x,
        by = list(fold_dat_shuffle_agg$Group.2),
        FUN = sd,
        na.rm = TRUE
      )
    colnames(fold_dat_shuffle_sd_cell) <-
      c("Cell_Line", "SD_Shuffle")
    colnames(fold_dat_shuffle_mean_cell) <-
      c("Cell_Line", "MEAN_FC_Shuffle")
    fold_dat_sd_cell <-
      rbind(fold_dat_sd_cell, fold_dat_shuffle_sd_cell)
    fold_dat_mean_cell <-
      rbind(fold_dat_mean_cell, fold_dat_shuffle_mean_cell)
  }
}

# write_delim(fold_dat_mean_cell,"Data/fold_dat_shuffle_meanFC_Wang.txt",delim = "\t")

# write_delim(fold_dat_sd_cell, "Data/fold_dat_shuffle_sdFC_Wang.txt", delim = "\t")

fold_dat_mean_cell <-
  read.delim("Data/fold_dat_shuffle_meanFC_Wang.txt")

fold_dat_sd_cell <-
  read.delim("Data/fold_dat_shuffle_sdFC_Wang.txt")

head(fold_dat_sd_cell)

head(fold_dat_mean_cell)

fold_dat_sd_cell_temp <- fold_dat_sd_cell

fold_dat_sd_cell_temp <-
  aggregate(
    fold_dat_sd_cell_temp$SD_Shuffle,
    by = list(fold_dat_sd_cell_temp$Cell_Line),
    FUN = mean,
    na.rm = TRUE
  )

colnames(fold_dat_sd_cell_temp) <- c("Cell_Line", "SD_Shuffle_Mean")

fold_dat_mean_cell_temp <- fold_dat_mean_cell

fold_dat_mean_cell_temp <-
  aggregate(
    fold_dat_mean_cell_temp$MEAN_FC_Shuffle,
    by = list(fold_dat_mean_cell_temp$Cell_Line),
    FUN = mean,
    na.rm = TRUE
  )

colnames(fold_dat_mean_cell_temp) <-
  c("Cell_Line", "MEAN_FC_Shuffle_Mean")

fold_dat_mean <-
  aggregate(
    Wang_FC_combine$FC,
    by = list(Wang_FC_combine$GENE, Wang_FC_combine$Type),
    FUN = mean,
    na.rm = TRUE
  )

colnames(fold_dat_mean)  <- c("GENE", "Cell_Line", "MEAN_FC")

fold_dat_results <- merge(fold_dat_mean, fold_dat_mean_cell_temp)

fold_dat_results <- merge(fold_dat_results, fold_dat_sd_cell_temp)

fold_dat_count <- Wang_FC_combine %>% dplyr::count(GENE, REAGENT_ID)

temp <- Wang_FC_combine %>% filter(FC > 0)

fold_dat_count_above <- temp %>% dplyr::count(GENE, Cell_Line)

colnames(fold_dat_count_above) = c("GENE", "match", "n_above")

fold_dat_count <-
  merge(fold_dat_count, fold_dat_count_above, all.x = TRUE)

fold_dat_count$n_above[is.na(fold_dat_count$n_above)] = 0

rm(fold_dat_count_above, temp)

colnames(fold_dat_count)[2] = "Cell_Line"

fold_dat_count$percentage = fold_dat_count$n_above / fold_dat_count$n

fold_dat_results <-
  merge(fold_dat_results, fold_dat_count, all.x = TRUE)

fold_dat_results$percentage = round(fold_dat_results$percentage, digits = 5)

Wang_FC_cells <-
  Wang_FC_combine %>% dplyr::select(Type, Cell_Line) %>% unique()

colnames(fold_dat_results)[1] = "Type"

fold_dat_results <- merge(fold_dat_results, Wang_FC_cells)

# write_delim(fold_dat_results, "Data/Wang_Shuffle_Corrected_FC.txt", delim = "\t")

head(fold_dat_results)
```


##Clear
```{r clear}
rm(list = ls())
```