---
title: "Figure6_with_supp"
output: 
  html_document:
    fig_width: 10
    fig_height: 10
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The following markdown document contains the majority of code used to generate figures displayed in Figure 6,  and Supplementary Figure 9. The code is not optimized for markdown viewership, as each plot was individually saved as a pdf.

##Session Info
```{r session}
rm(list = ls())
if (is.integer(dev.list())){dev.off()}
cat("\014")
set.seed(1)
source("functions.R")
sessionInfo()
```

```{r data_load}
avana_res <- read.delim("Data/avana_output_v2.txt")
cell_line_key <- read_csv("Data/DepMap-2018q4-celllines.csv")
cna_transposed_AML <- read.delim("Data/cna_transposed_AML.txt")
```

###Initial Data Manipulation for Figure 6A
```{r data_manipulation}
cell_key <- cell_line_key %>% dplyr::select(DepMap_ID,`Subtype Disease`,CCLE_Name)
colnames(cell_key) = c('Cell_Line',"Subtype","CCLE")

rownames(cna_transposed_AML) <- cna_transposed_AML$STUDY_ID
cna_transposed_AML$STUDY_ID <- NULL
CNA_AML <- cna_transposed_AML %>% t() %>% as.data.frame()

FLT3_ITD <- c("ACH-000045","ACH-000362","ACH-000218") ### From DMSZ website

###filtering for genes from Figure 5 network
AML_Heatmap <- avana_res %>% filter(GENE %in%  c("FASN","CHP1","ACACA","GPAT4","SREBF1","CPT2","CRLS1","SQLE","ACLY","SCD","FABP5")) %>% dplyr::select(GENE,Cell_Line,Mod_Z_Score)
AML_Heatmap <- spread(AML_Heatmap,GENE,Mod_Z_Score)
AML_Heatmap <- merge(AML_Heatmap,cell_key)
AML_Heatmap <- AML_Heatmap %>% filter(Subtype == "Acute Myelogenous Leukemia (AML)")

###we looked at various AML subtypes, and didn't observe anything specific corresponding to FASTS
temp <- AML_Heatmap %>% dplyr::select(Cell_Line, CCLE)
CNA_AML <- CNA_AML %>% filter(SAMPLE_ID %in% AML_Heatmap$CCLE) %>% dplyr::select(-c(IDH2,TET2,NRAS,NPM1,BAX,DNMT3A,GATA2))
colnames(CNA_AML)[1] <- "CCLE"
CNA_AML <- merge(temp,CNA_AML)

###simplified for manuscript
muts <- c("FLT3","TP53","NRAS","KRAS","KMT2A")
colnames(CNA_AML)
muts_data <- avana_res %>% filter(GENE %in% muts) %>% filter(Cell_Line %in% AML_Heatmap$Cell_Line) %>% dplyr::select(Cell_Line,GENE,mut) %>% unique()
muts_data <- spread(muts_data,GENE,mut)

muts_data$FLT3_ITD <- 0
muts_data$FLT3_ITD[muts_data$Cell_Line %in% FLT3_ITD] <- 1

rownames(AML_Heatmap) <- map(strsplit(AML_Heatmap$CCLE,"_",fixed = TRUE), 1) %>% unlist()
AML_Heatmap <- AML_Heatmap %>% dplyr::select(-Cell_Line,-Subtype,-CCLE)

###color schemes for heatmap
col_fun = colorRamp2(c(-10, 0, 10), c("#e60505",'white',"#69cfff"))
col_fun2 = colorRamp2(c(0, 1), c("#f2eded","#de962a"))
col = list(foo = col_fun2)

temp1 <- muts_data %>% gather(GENE,mut,-Cell_Line)
temp2 <- CNA_AML %>% dplyr::select(-c(CCLE,CEBPA,RUNX1,IDH1)) %>% gather(GENE,mut,-Cell_Line)
temp1$key <- paste(temp1$GENE,temp1$Cell_Line)
temp2 <- temp2 %>% filter(mut != 0)
temp2$key <- paste(temp2$GENE,temp2$Cell_Line)
temp1 <- temp1 %>% filter(key %!in% temp2$key)
temp2$mut <- as.numeric(temp2$mut)
muts_data <- rbind(temp1,temp2) %>% dplyr::select(-key) %>% spread(GENE,mut)

# Mutation: - 1
# Amp: 2
# Delete: -2
# Keeping Mut for both TSG & Amp, deletion for TSG, Amp for oncogenic 

##spot checked to make sure no overlap prior
muts_data$FLT3 <- muts_data$FLT3 + muts_data$FLT3_ITD
muts_data$FLT3[muts_data$FLT3 == -2] <- 0
muts_data$FLT3[muts_data$FLT3 == 2] <- 1

muts_data$KRAS[muts_data$KRAS == -2] <- 0
muts_data$KRAS[muts_data$KRAS == 2] <- 1

muts_data$NRAS[muts_data$NRAS == -2] <- 0
muts_data$NRAS[muts_data$NRAS == 2] <- 1

muts_data$KMT2A[muts_data$KMT2A == 2] <- 0
muts_data$KMT2A[muts_data$KMT2A == -2] <- 1

muts_data$TP53[muts_data$TP53 == 2] <- 0
muts_data$TP53[muts_data$TP53 == -2] <- 1
```

```{r heatmap_6A}
ha1 <-
  HeatmapAnnotation(
    foo = cbind(
      TP53 = muts_data$TP53,
      NRAS = muts_data$NRAS,
      KRAS = muts_data$KRAS,
      FLT3_ITD = muts_data$FLT3,
      KMT2A = muts_data$KMT2A
    ),
    annotation_name_side = "right",
    col = col,
    show_legend = c("foo" = FALSE),
    show_annotation_name = c(foo = TRUE),
    # only turn off `bar`
    height = unit(4, "cm"),gp = gpar(fontsize = 10),
    name = "foo_ann"
  )

Heatmap(
  as.matrix(t(AML_Heatmap)),col = col_fun, cluster_rows = TRUE,top_annotation = ha1,
  cluster_columns = TRUE,show_heatmap_legend = TRUE,
  row_names_gp = gpar(fontsize = 20))
```


###Survival Analysis
Resetting - Shifting gears to survival analysis
```{r reset_1}
rm(list = ls())
if (is.integer(dev.list())){dev.off()}
cat("\014")
set.seed(1)
source("functions.R")
library(survival)
library(survminer)
```


Loading in Target data used
```{r survival_data}
TARGET <- read.delim("Data/TARGET_Complete.txt")
GDC_TARGET_Age <- read.delim("Data/GDC_Target_Age.tsv") %>%
  dplyr::select(sample,Age.at.Diagnosis.in.Days)
TARGET_sample_meta <- read.delim("Data/TARGET_sample_meta.tsv")
```


Brief data manipualtion and checking the Hazard's assumption (supp fig 9).
```{r surv_data_manip}
colnames(TARGET_sample_meta)[5] <- "Patient"
colnames(GDC_TARGET_Age) <- c("Patient","Age")
genes <- c("ACACA","ACLY","CHP1","CPT2","CRLS1","FABP5","FASN","GPAT4","SCD","SQLE","SREBF1")

TARGET <- TARGET %>% filter(GENE %in% genes)

TARGET <- merge(TARGET,GDC_TARGET_Age) %>% spread(GENE,Exp)

TARGET$Age_Years <- TARGET$Age/365

TARGET <- merge(TARGET,TARGET_sample_meta) %>% droplevels()

TARGET <- TARGET %>% filter(!grepl("Recurrent",sample_type)) %>% droplevels()

fit.coxph <- coxph(Surv(OS.time, X_EVENT)~CHP1,data = TARGET)
test.ph <- cox.zph(fit.coxph)
ggcoxzph(test.ph)

fit.coxph <- coxph(Surv(OS.time, X_EVENT)~GPAT4, data = TARGET)
test.ph <- cox.zph(fit.coxph)
ggcoxzph(test.ph)

fit.coxph <- coxph(Surv(OS.time, X_EVENT)~FASN, data = TARGET)
test.ph <- cox.zph(fit.coxph)
ggcoxzph(test.ph)

fit.coxph <- coxph(Surv(OS.time, X_EVENT)~ACACA, data = TARGET)
test.ph <- cox.zph(fit.coxph)
ggcoxzph(test.ph)

fit.coxph <- coxph(Surv(OS.time, X_EVENT)~SQLE, data = TARGET)
test.ph <- cox.zph(fit.coxph)
ggcoxzph(test.ph)

fit.coxph <- coxph(Surv(OS.time, X_EVENT)~CPT2, data = TARGET)
test.ph <- cox.zph(fit.coxph)
ggcoxzph(test.ph)

fit.coxph <- coxph(Surv(OS.time, X_EVENT)~CPT2, data = TARGET)
test.ph <- cox.zph(fit.coxph)
ggcoxzph(test.ph)

fit.coxph <- coxph(Surv(OS.time, X_EVENT)~ACLY, data = TARGET)
test.ph <- cox.zph(fit.coxph)
ggcoxzph(test.ph)

fit.coxph <- coxph(Surv(OS.time, X_EVENT)~SREBF1, data = TARGET)
test.ph <- cox.zph(fit.coxph)
ggcoxzph(test.ph)

fit.coxph <- coxph(Surv(OS.time, X_EVENT)~SCD, data = TARGET)
test.ph <- cox.zph(fit.coxph)
ggcoxzph(test.ph)

fit.coxph <- coxph(Surv(OS.time, X_EVENT)~CRLS1, data = TARGET)
test.ph <- cox.zph(fit.coxph)
ggcoxzph(test.ph)

fit.coxph <- coxph(Surv(OS.time, X_EVENT)~FABP5, data = TARGET)
test.ph <- cox.zph(fit.coxph)
ggcoxzph(test.ph)

fit.coxph <- coxph(Surv(OS.time, X_EVENT)~Age_Years, data = TARGET)
test.ph <- cox.zph(fit.coxph)
ggcoxzph(test.ph)
```


Examining the HR for each variable + forest plot
```{r surv_data_forest}
covariates <- c(genes,"Age_Years")
univ_formulas <- sapply(covariates, function(x) as.formula(paste('Surv(OS.time, X_EVENT)~', x)))

univ_models <- lapply( univ_formulas, function(x){coxph(x, data = TARGET)})
# Extract data, function adapted from http://www.sthda.com/english/wiki/cox-proportional-hazards-model
univ_results <- lapply(univ_models,
                       function(x){ 
                         x <- summary(x)
                         p.value<-signif(x$wald["pvalue"], digits=2)
                         wald.test<-signif(x$wald["test"], digits=2)
                         beta<-signif(x$coef[1], digits=2);#coeficient beta
                         HR <-signif(x$coef[2], digits=2);#exp(beta)
                         HR.confint.lower <- signif(x$conf.int[,"lower .95"], 2)
                         HR.confint.upper <- signif(x$conf.int[,"upper .95"],2)
                         HR_comb <- paste0(HR, " (",
                                      HR.confint.lower, "-", HR.confint.upper, ")")
                         res<-c(beta, HR, wald.test, p.value,HR.confint.lower,HR.confint.upper,HR_comb)
                         names(res)<-c("beta", "HR", "wald.test", 
                                       "p.value","HR_CI_low","HR_CI_high","HR_comb")
                         return(res)
                         #return(exp(cbind(coef(x),confint(x))))
                       })

res <- t(as.data.frame(univ_results, check.names = FALSE)) %>% as.data.frame()

res$row_a <- paste(row.names(res),", HR = ",res$HR_comb,", p = ",res$p.value,sep = "")

res <- res[covariates,]

res$row_a <- factor(res$row_a, levels = res$row_a) %>% fct_rev()

ggplot(res, aes(x = HR, y = row_a)) +
  geom_point(size = 3,stat = "identity") + 
  geom_errorbar(aes(xmax = HR_CI_high, xmin = HR_CI_low), size = 0.5) + 
  xlab("Hazard Ratio") + ylab("") + theme_cowplot() 

```

Plotting Survival Curves
```{r GPAT4_curve}
TARGET_temp <- TARGET %>% unique()

gene_test <- "GPAT4"

gene_test_qs <- quantile(x = TARGET[,gene_test],c(0.75))

TARGET_gene_q1_q2_q3 <- TARGET_temp %>% filter(TARGET[,gene_test] < gene_test_qs[1]) %>% droplevels() 
TARGET_gene_q4 <- TARGET_temp %>% filter(TARGET[,gene_test] >= gene_test_qs[1]) %>% droplevels() 

q1_3 <- nrow(TARGET_gene_q1_q2_q3)
q4 <- nrow(TARGET_gene_q4)

TARGET_temp$type <- NULL
TARGET_temp$type <- paste(gene_test,"Other",q1_3,sep = "_")
TARGET_temp$type[TARGET_temp$Patient %in% TARGET_gene_q4$Patient] = paste(gene_test,"q4",q4,sep = "_")

fit <- survfit(Surv(OS.time, X_EVENT) ~ type, data = TARGET_temp)

ggsurvplot(fit,
           conf.int = FALSE,
           risk.table.col = "strata", # Change risk table color by groups
           ggtheme = theme_bw(), # Change ggplot2 theme
           # palette = c("#E7B800", "#2E9FDF"),
           pval = TRUE) + ggtitle(gene_test)

```

```{r CHP1_curve}
gene_test <- "CHP1"

gene_test_qs <- quantile(x = TARGET[,gene_test],c(0.75))

TARGET_gene_q1_q2_q3 <- TARGET_temp %>% filter(TARGET[,gene_test] < gene_test_qs[1]) %>% droplevels() 
TARGET_gene_q4 <- TARGET_temp %>% filter(TARGET[,gene_test] >= gene_test_qs[1]) %>% droplevels() 

q1_3 <- nrow(TARGET_gene_q1_q2_q3)
q4 <- nrow(TARGET_gene_q4)

TARGET_temp$type <- NULL
TARGET_temp$type <- paste(gene_test,"Other",q1_3,sep = "_")
TARGET_temp$type[TARGET_temp$Patient %in% TARGET_gene_q4$Patient] = paste(gene_test,"q4",q4,sep = "_")

fit <- survfit(Surv(OS.time, X_EVENT) ~ type, data = TARGET_temp)

ggsurvplot(fit,
           conf.int = FALSE,
           risk.table.col = "strata", # Change risk table color by groups
           ggtheme = theme_bw(), # Change ggplot2 theme
           # palette = c("#E7B800", "#2E9FDF"),
           pval = TRUE) + ggtitle(gene_test)

```

Resetting again to bring up age of various AML cohorts
```{r reset_2}
rm(list = ls())
if (is.integer(dev.list())){dev.off()}
cat("\014")
set.seed(1)
source("functions.R")
```

```{r AML_ages}
GDC_TARGET_Age <- read.delim("Data/GDC_Target_Age.tsv") 
colnames(GDC_TARGET_Age) <- c("Sample","Samples","Age_Days","Exp")
GDC_TARGET_Age$Age <- round(GDC_TARGET_Age$Age_Days/365,digits =0)
GDC_TARGET_Age <- GDC_TARGET_Age %>% dplyr::select(Age,Sample,Exp)
GDC_TARGET_Age$Type <- "TARGET"

OSHU_AML_Age <- read_csv("Data/AML_OSHU_Age.csv")
colnames(OSHU_AML_Age) <- c("Age","Sample","Exp")
OSHU_AML_Age$Type <- "OSHU"

TCGA_AML_Age <- read.delim("Data/LAML_clinical_meta.tsv")
TCGA_AML_Age <- TCGA_AML_Age %>% dplyr::select(age_at_initial_pathologic_diagnosis,sample,FASN)
colnames(TCGA_AML_Age) <- c("Age","Sample","Exp")
TCGA_AML_Age$Type <- "TCGA"

AML_Age_Data <- do.call("rbind", list(TCGA_AML_Age,GDC_TARGET_Age,OSHU_AML_Age))

###Filtering for patients with expression data
AML_Age_Data <- AML_Age_Data[complete.cases(AML_Age_Data$Exp), ]

AML_Age_Data %>% ggplot(aes(Type,as.numeric(Age),color = Type)) + geom_beeswarm() + theme_Publication() + ylab("Age") + xlab("")
```


Resetting again to bring up to observed difference in age of observed phenotype
```{r reset_3}
rm(list = ls())
if (is.integer(dev.list())){dev.off()}
cat("\014")
set.seed(1)
source("functions.R")
```

```{r age_cell_line}
avana_res <- read.delim("Data/avana_output_v2.txt") %>% filter(GENE == "FASN")
AML_age <- read.delim("Data/AML_age.txt") ### curated manually from cellasaurus 

avana_res <- avana_res %>% dplyr::select(Cell_Line,Mod_Z_Score)

avana_res <- merge(avana_res,AML_age,all.x = TRUE)

avana_res %>% ggplot(aes(Mod_Z_Score,Age)) + geom_point(size = 2) + theme_Publication() + xlab("FASN Shuffled Z-Score")

```