---
title: "Figure2_with_supp"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The following markdown document contains the majority of code used to generate figures displayed in Figure 2 and Supplemental Figure 4. Figure 2B (network pipeline) was made using Illustrator, and Figure 2C (network) was made using Cytoscape.

```{r session}
rm(list = ls())
if (is.integer(dev.list())){dev.off()}
cat("\014")
set.seed(1)
source("functions.R")
sessionInfo()
```

##Figure 2A - Complex heatmap demonstrating network approach
The plot was made twice and then just overlaid in illustrator. Legends made with code from stackoverflow (https://stackoverflow.com/questions/9314658/colorbar-from-custom-colorramppalette)
```{r complex_heatmap_fish_fdr}

###Complex heatmap 2A

avana_res <- read.delim("Data/avana_output_v2.txt")
temp_hits <- avana_res %>% filter(hit == 1) %>% droplevels()

picked_genes <-
  c(
    "TP53",
    "TP53BP1",
    "CDKN1A",
    "CHEK2",
    "MAP4K4",
    "TAOK1",
    "KIRREL1",
    "NF2",
    "TSC1",
    "TSC2",
    "PTEN",
    "AMOTL2",
    "LATS2",
    "PDCD10",
    "NRP1"
  )

temp_hits <-
  avana_res %>% filter(GENE %in% picked_genes) %>% #filter(Cosmic_TSG == 1) %>%
  droplevels() %>% dplyr::select(GENE, Cell_Line, hit) %>% unique()

g1 = c()
g2 = c()
Freq = c()

for (i in 1:length(picked_genes)) {
  for (j in i:length(picked_genes)) {
    if (i != j) {
      gene1 = picked_genes[i]
      gene2 = picked_genes[j]
      temp_cells <-
        temp_hits %>% filter(GENE %in% c(gene1, gene2)) %>% filter(hit == 1) %>% droplevels() %>% pull(Cell_Line) %>% as.vector()
      num <- length(temp_cells[duplicated(temp_cells)])
      g1 = c(g1, gene1)
      g2 = c(g2, gene2)
      Freq = c(Freq, num)
      
    }
  }
}

obs <- data.frame(g1, g2, Freq)
obs2 <- data.frame(g2, g1, Freq)
colnames(obs2) = c("g1", "g2", "Freq")
obs <- rbind(obs, obs2)

fisher_results <- read.delim("Data/fisher_edges_tsg_v2_2_05.txt")
fisher_results$FDR = p.adjust(fisher_results$fish_p, method = "fdr")

fisher_results <-
  fisher_results %>% filter(g1 %in% picked_genes) %>% filter(g2 %in% picked_genes) %>% dplyr::select(g1, g2, FDR) %>% spread(g2, FDR)

rownames(fisher_results) <- fisher_results$g1
fisher_results$g1 <- NULL
fisher_results[is.na(fisher_results)] <- 0

dist.eucl <- dist(fisher_results, method = "euclidean")

mat <- obs %>% spread(g2, Freq)
rownames(mat) <- mat$g1
mat$g1 <- NULL

my_palette <-
  colorRampPalette(c("#6c74d9", "#bdbfd9", "white"))(n = 100)

fisher_results_t <- as.matrix(fisher_results)
head(fisher_results_t)
head(mat)

cluster = hclust(dist.eucl)

mat <- obs %>% spread(g2, Freq)
rownames(mat) <- mat$g1
mat$g1 <- NULL
mat <- mat[cluster$labels, cluster$labels]

mat

fisher_results_t <- round(as.matrix(fisher_results), 3)

my_palette <-
  colorRampPalette(c("#6c74d9", "#cacbd9", "white"))(n = 100)

heatmap.2(
  fisher_results_t,
  Rowv = as.dendrogram(cluster),
  # apply default clustering method
  Colv = as.dendrogram(cluster),
  cellnote = fisher_results_t,
  col = my_palette,
  notecol = "black",
  density.info = "none",
  key = FALSE,
  trace = "none"
)

# color.bar <-
#   function(lut,
#            min,
#            max = -min,
#            nticks = 11,
#            ticks = seq(min, max, len = nticks),
#            title = '') {
#     scale = (length(lut) - 1) / (max - min)
#     
#     dev.new(width = 1.75, height = 5)
#     plot(
#       c(0, 10),
#       c(min, max),
#       type = 'n',
#       bty = 'n',
#       xaxt = 'n',
#       xlab = '',
#       yaxt = 'n',
#       ylab = '',
#       main = title
#     )
#     axis(2, ticks, las = 1)
#     for (i in 1:(length(lut) - 1)) {
#       y = (i - 1) / scale + min
#       rect(0, y, 10, y + 1 / scale, col = lut[i], border = NA)
#     }
#   }
# color.bar(my_palette, min = 0.000, max = 1.000)

# color.bar(my_palette, min = 0, max = 45)
```

Co-Occurence Heatmap
```{r complex_heatmap_counts}
my_palette <-
  colorRampPalette(c("white", "#c4a068", "#cf953a"))(n = 45)
heatmap.2(
  as.matrix(mat),
  Rowv = as.dendrogram(cluster),
  # apply default clustering method
  Colv = as.dendrogram(cluster),
  cellnote = mat,
  col = my_palette,
  notecol = "black",
  trace = "none",
  key = FALSE
)
```

##Supplemental Figure 4 - HumanNet enrichment scoring
Includes empirical p-value calculation.
```{r humannet_enrich}
rm(list = ls())
if (is.integer(dev.list())) {
  dev.off()
}
cat("\014")

set.seed(1)
source("functions.R")

HS.CE <-
  read.delim("Data/HS-CE.tsv",
             header = FALSE,
             comment.char = "#")
HumanNet.FN <- read.delim("Data/HumanNet-FN.tsv", header = FALSE)

###Human Net files, CE = Coessentiality, FN is Human net without coessential network.

fisher_results <- read.delim("Data/fisher_edges_tsg_v2_2_05.txt")
fisher_results_HuNet <-
  read.delim("./Data/fisher_results_res_fdr_0.01_2_7_20.txt")
colnames(HumanNet.FN) = c("GENE1", "GENE2", "FN_Score")

V1 <- as.vector(as.character(fisher_results_HuNet$g1)) #%>% unique()
entrez_IDS <- mapIds(org.Hs.eg.db, V1, 'ENTREZID', 'SYMBOL')
fisher_results_HuNet$GENE1_entrez_ID = entrez_IDS

V2 <- as.vector(as.character(fisher_results_HuNet$g2)) #%>% unique()
entrez_IDS <- mapIds(org.Hs.eg.db, V2, 'ENTREZID', 'SYMBOL')
fisher_results_HuNet$GENE2_entrez_ID = entrez_IDS
fisher_results_HuNet$Hunet = 0

V1 <- as.vector(as.character(fisher_results$g1)) #%>% unique()
entrez_IDS <- mapIds(org.Hs.eg.db, V1, 'ENTREZID', 'SYMBOL')
fisher_results$GENE1_entrez_ID = entrez_IDS

V2 <- as.vector(as.character(fisher_results$g2)) #%>% unique()
entrez_IDS <- mapIds(org.Hs.eg.db, V2, 'ENTREZID', 'SYMBOL')
fisher_results$GENE2_entrez_ID = entrez_IDS
fisher_results$Hunet = 0
hunetgenes <- c(HumanNet.FN$GENE1, HumanNet.FN$GENE2) %>% unique()

rm(V1, V2, entrez_IDS)

###Identifying genes within human net

fisher_results <-
  fisher_results %>% filter(GENE1_entrez_ID %in% hunetgenes) %>% filter(GENE2_entrez_ID %in% hunetgenes)
fisher_results_HuNet <-
  fisher_results_HuNet %>% filter(GENE1_entrez_ID %in% hunetgenes) %>% filter(GENE2_entrez_ID %in% hunetgenes)
fisher_results_fil <- fisher_results %>% filter(g1 == "")

genes <-
  unique(c(
    as.character(fisher_results$g1),
    as.character(fisher_results$g2)
  ))
gene_entrez <-
  unique(c(
    as.character(fisher_results$GENE1_entrez_ID),
    as.character(fisher_results$GENE2_entrez_ID)
  ))
HumanNet.FN <-
  HumanNet.FN %>% filter(GENE1 %in% gene_entrez) %>% filter(GENE2 %in% gene_entrez)

###Checking every possible edge to see if its found within human net. 
for (i in 1:length(genes)) {
  gene1 = genes[i]
  #print(gene1)
  if (i != length(genes)) {
    for (k in (i + 1):length(genes)) {
      gene2 = genes[k]
      fisher_results_temp <-
        fisher_results %>% filter(g1 == gene1, g2 == gene2)
      fisher_results_fil = rbind(fisher_results_fil, fisher_results_temp)
    }
  }
}

head(fisher_results_fil)

###
sum_edges <- c()
#for (n in 1:10000){
###randomly selecting n edges (fishes network) to see enrichment possibility, ran once for demonstration 
for (n in 1:1) {
  print(n)
  temp <-
    sample_n(fisher_results_fil, size = nrow(fisher_results_HuNet))
  for (i in 1:nrow(fisher_results_HuNet)) {
    #print(i)
    GENE1_entrez = temp[i, 5]
    GENE2_entrez = temp[i, 6]
    temp_hunet <-
      HumanNet.FN %>% filter(GENE1 == GENE1_entrez) %>% filter(GENE2 == GENE2_entrez)
    if (nrow(temp_hunet) != 0) {
      temp[i, 7] = 1
    }
    temp_hunet2 <-
      HumanNet.FN %>% filter(GENE1 == GENE2_entrez) %>% filter(GENE2 == GENE1_entrez)
    if (nrow(temp_hunet2) != 0) {
      temp[i, 7] = 1
    }
  }
  sum_edges <-
    c(sum_edges, (sum(temp$Hunet) / nrow(fisher_results_HuNet)))
}

###Checking resulting network human net overlap
for (i in 1:nrow(fisher_results_HuNet)) {
  #print(i)
  GENE1_entrez = fisher_results_HuNet[i, 7]
  GENE2_entrez = fisher_results_HuNet[i, 8]
  temp_hunet <-
    HumanNet.FN %>% filter(GENE1 == GENE1_entrez) %>% filter(GENE2 == GENE2_entrez)
  if (nrow(temp_hunet) != 0) {
    fisher_results_HuNet[i, 9] = 1
  }
  temp_hunet2 <-
    HumanNet.FN %>% filter(GENE1 == GENE2_entrez) %>% filter(GENE2 == GENE1_entrez)
  if (nrow(temp_hunet2) != 0) {
    fisher_results_HuNet[i, 9] = 1
  }
}

###Checking Coessentiality network overlap
fisher_results_HuNet$CE = 0
for (i in 1:nrow(fisher_results_HuNet)) {
  #print(i)
  GENE1_entrez = fisher_results_HuNet[i, 7]
  GENE2_entrez = fisher_results_HuNet[i, 8]
  temp_hunet <-
    HS.CE %>% filter(V1 == GENE1_entrez) %>% filter(V2 == GENE2_entrez)
  if (nrow(temp_hunet) != 0) {
    fisher_results_HuNet[i, 10] = 1
  }
  temp_hunet2 <-
    HS.CE %>% filter(V1 == GENE2_entrez) %>% filter(V2 == GENE1_entrez)
  if (nrow(temp_hunet2) != 0) {
    fisher_results_HuNet[i, 10] = 1
  }
}

real_sum_edges <-
  sum(fisher_results_HuNet$Hunet) / nrow(fisher_results_HuNet)

sd_sum_edges <- sd(sum_edges)
mean_sum_edges <- mean(sum_edges)

sd_sum_edges <- sd(sum_edges)

###used for the lines in supplemental figure 3
real_sum_edges <-
  sum(fisher_results_HuNet$Hunet) / nrow(fisher_results_HuNet)

real_CE_edges <-
  sum(fisher_results_HuNet$CE) / nrow(fisher_results_HuNet)

hunet_data <- data.frame(sum_edges)
#save(sum_edges, real_sum_edges,real_CE_edges , file = "./Data/Hunet_comparison.Rdata")
#unlink("./Data/Hunet_comparison.Rdata")

######only ran once for demonstration, loading in original data. 

rm(list = ls())
if (is.integer(dev.list())) {
  dev.off()
}
cat("\014")
set.seed(1)
source("functions.R")

load("Data/Hunet_comparison.Rdata", .GlobalEnv)

hunet_data <- data.frame(sum_edges)
```

```{r human_net_plot}
hunet_data %>% ggplot(aes(sum_edges)) + geom_histogram(bins = 30) + theme_Publication() +
  geom_vline(xintercept = real_CE_edges) + geom_vline(xintercept = real_sum_edges) + ylab("Edge Count") +
  xlab("Percentage of Edge Coverage in HumaNet")
```

```{r human_net_cutoff}

result_df <- read.delim("Data/Human_net_cutoff_results.txt")

result_df %>% ggplot(aes(x = interval_Z,y = percent_edges,size = gene_network)) + geom_point() + theme_Publication() + xlab("Interval Shuffled Z-Score") + ylab("Percent Edges Found in Human Net") + geom_vline(xintercept = 5.235, color = "red")
```

##Figure 2D - Network Ornaments 
First ornament is commented, however other ornaments follow same code chunks, with exception of FASN. FASN contains fisher's test check with respect to AML. 
```{r jak_stat}
rm(list = ls())
if (is.integer(dev.list())){dev.off()}
cat("\014")

set.seed(1)
source("functions.R")

avana_res <- read.delim("Data/avana_output_v2.txt")
cell_line_key <- read_csv("Data/DepMap-2018q4-celllines.csv")

Mod_Z_pr_values <- read.delim("Data/Mod_Z_pr_values.txt") ### Taken from figure 1 code.
Mod_Z_pr_values <- Mod_Z_pr_values %>% dplyr::select(-Recall)
Mod_Z_pr_values$Precision <- round(Mod_Z_pr_values$Precision,digits = 2)

###Aggregating precision scores used to color in the box

Mod_Z_pr_values <- aggregate(
  Mod_Z_pr_values$Precision,
  by = list(Mod_Z_pr_values$Score),
  FUN = mean,
  na.rm = TRUE
)

colnames(Mod_Z_pr_values) = c("Mod_Z_Score","FDR")
###FDR from precision
Mod_Z_pr_values$FDR = 1-Mod_Z_pr_values$FDR 

###color used for heatmap ornaments
tsg_green <- "#699186"

############################ jak-stat2
picked_genes <- c("JAK1","STAT2","IRF9","TYK2")

###creating binary matrix of hits
temp_hits <- avana_res %>% filter(GENE %in% picked_genes) %>% #filter(Cosmic_TSG == 1) %>%
  droplevels() %>% dplyr::select(GENE,Cell_Line,hit) %>% unique() %>% spread(Cell_Line,hit)

###removing 0 columns
temp <- temp_hits[-1][colSums(temp_hits[-1]) > 0]
temp_hits <- temp_hits %>% dplyr::select(GENE,colnames(temp))
rownames(temp_hits) = temp_hits$GENE
temp_hits$GENE = NULL

JAK1_Cells <- avana_res %>% filter(GENE == "JAK1") %>% filter(hit == 1) %>% pull(Cell_Line) %>% droplevels() %>% as.vector()
STAT2_Cells <- avana_res %>% filter(GENE == "STAT2") %>% filter(hit == 1) %>% pull(Cell_Line) %>% droplevels() %>% as.vector()
TYK2_Cells <- avana_res %>% filter(GENE == "TYK2") %>% filter(hit == 1) %>% pull(Cell_Line) %>% droplevels() %>% as.vector()
IRF9_Cells <- avana_res %>% filter(GENE == "IRF9") %>% filter(hit == 1) %>% pull(Cell_Line) %>% droplevels() %>% as.vector()

###ordering the heatmap
temp_hits <- temp_hits[unique(c(IRF9_Cells,STAT2_Cells,TYK2_Cells,JAK1_Cells))]
order = c("IRF9","STAT2","TYK2","JAK1")
col_order <- colSums(temp_hits) %>% sort(decreasing = TRUE)
###Matching disease type for annotation bar
cells <- cell_line_key %>% filter(DepMap_ID %in% names(col_order)) %>% droplevels() %>% pull(`Primary Disease`) %>% toupper()
temp_hits <- temp_hits[match(order, rownames(temp_hits)),names(col_order)]

col_order <- colSums(temp_hits) %>% sort(decreasing = TRUE)
cells <- cell_line_key %>% filter(DepMap_ID %in% names(col_order)) %>% droplevels() %>% pull(`Primary Disease`) %>% toupper()
cells <- color.bar(cells)

temp_hits <- temp_hits[match(order, rownames(temp_hits)),names(col_order)]
col = list(foo = cells)

###selecting z-scores now for color range observed. This gives gradient in heatmap
temp_z_score <- avana_res %>% filter(GENE %in% picked_genes) %>% filter(Cell_Line %in% colnames(temp_hits)) %>%
  droplevels() %>% dplyr::select(GENE,Cell_Line,Mod_Z_Score) #%>% unique() %>% spread(Cell_Line,Mod_Z_Score)

temp_z_score$Mod_Z_Score <- round(temp_z_score$Mod_Z_Score, digits = 2) 

###Merging shuffled z-scores to FDR values
a=data.table(Mod_Z_Data=c(temp_z_score$Mod_Z_Score))
a[,merge:=Mod_Z_Data]

b=data.table(Mod_Z_PR=c(Mod_Z_pr_values$Mod_Z_Score))
b[,merge:=Mod_Z_PR]

setkeyv(a,c('merge'))
setkeyv(b,c('merge'))

Merge_a_b=b[a,roll='nearest']

colnames(Merge_a_b)[1] <- "Mod_Z_Score_match"
colnames(Merge_a_b)[2] <- "Mod_Z_Score"

temp_z_score <- merge(temp_z_score,Merge_a_b) %>% dplyr::select(GENE,Cell_Line,Mod_Z_Score_match)
colnames(temp_z_score)[3] <- "Mod_Z_Score"

temp_z_score <- merge(temp_z_score,Mod_Z_pr_values,all.x = TRUE)

temp_z_score <- temp_z_score %>% unique() %>% dplyr::select(-Mod_Z_Score) %>% spread(Cell_Line,FDR)

rownames(temp_z_score) = temp_z_score$GENE
temp_z_score$GENE = NULL

temp_z_score <- temp_z_score[rownames(temp_hits),]
temp_z_score <- temp_z_score[,colnames(temp_hits)]

###color ramp, demonstrates values that are close to cutoff
cols = colorRamp2(c(0.0, 0.10,0.20,0.30,0.40,0.50), c(tsg_green,tsg_green,"white","white","white","white"))
#cols = colorRamp2(c( 0.25, 0.5,0.75, 1), c("white","white","white","#4A3EBA"))
#cols <- colorRampPalette(c("white","#3a393b"))(n = 1000)
ha1 <- HeatmapAnnotation(foo = cbind(Type = names(cells)),annotation_name_side = "right",
                         col = col, show_legend = c("foo" = TRUE),show_annotation_name = c(foo = TRUE), # only turn off `bar`
                         height = unit(1, "cm"),name = "foo_ann")

#pdf("./paper_figs_code/fig/3-jack_stat_Heatmap_common_scale.pdf",width = 10,height = 10)
# Heatmap(
#   as.matrix(temp_z_score),col = cols, cluster_rows = FALSE,cluster_columns = FALSE,top_annotation = ha1,
#   name = "foo",show_heatmap_legend = TRUE  #Colv=NA,scale = "none", col = cols,Rowv = NA
# )
#decorate_heatmap_body("foo", {grid.rect(gp = gpar(fill = "transparent", col = "black", lwd = 1))})
#dev.off()
```
```{r jak_stat_plot}
Heatmap(
  as.matrix(temp_z_score),col = cols, cluster_rows = FALSE,cluster_columns = FALSE,top_annotation = ha1,
  name = "foo",show_heatmap_legend = TRUE  #Colv=NA,scale = "none", col = cols,Rowv = NA
)
```

```{r aryl_ahr}
picked_genes <- c("AHR","ARNT")

temp_hits <- avana_res %>% filter(GENE %in% picked_genes) %>% #filter(Cosmic_TSG == 1) %>%
  droplevels() %>% dplyr::select(GENE,Cell_Line,hit) %>% unique() %>% spread(Cell_Line,hit)
temp <- temp_hits[-1][colSums(temp_hits[-1]) > 0]
temp_hits <- temp_hits %>% dplyr::select(GENE,colnames(temp))
rownames(temp_hits) = temp_hits$GENE
temp_hits$GENE = NULL

AHR_Cells <- avana_res %>% filter(GENE == "AHR") %>% filter(hit == 1) %>% pull(Cell_Line) %>% droplevels() %>% as.vector()
ARNT_Cells <- avana_res %>% filter(GENE == "ARNT") %>% filter(hit == 1) %>% pull(Cell_Line) %>% droplevels() %>% as.vector()

Other_Cells <- avana_res %>% filter(Cell_Line %in% colnames(temp)) %>%
  filter(Cell_Line %!in% c(AHR_Cells,ARNT_Cells)) %>%
  pull(Cell_Line) %>%droplevels() %>% as.vector() %>% unique()

temp_hits <- temp_hits[unique(c(ARNT_Cells,AHR_Cells))]
order = c("ARNT","AHR")

col_order <- colSums(temp_hits) %>% sort(decreasing = TRUE)
cells <- cell_line_key %>% filter(DepMap_ID %in% names(col_order)) %>% droplevels() %>% pull(`Primary Disease`) %>% toupper()
cells <- color.bar(cells)

temp_hits <- temp_hits[match(order, rownames(temp_hits)),names(col_order)]
col = list(foo = cells)

temp_z_score <- avana_res %>% filter(GENE %in% picked_genes) %>% filter(Cell_Line %in% colnames(temp_hits)) %>%
  droplevels() %>% dplyr::select(GENE,Cell_Line,Mod_Z_Score) #%>% unique() %>% spread(Cell_Line,Mod_Z_Score)

temp_z_score$Mod_Z_Score <- round(temp_z_score$Mod_Z_Score, digits = 2) 

a=data.table(Mod_Z_Data=c(temp_z_score$Mod_Z_Score))
a[,merge:=Mod_Z_Data]

b=data.table(Mod_Z_PR=c(Mod_Z_pr_values$Mod_Z_Score))
b[,merge:=Mod_Z_PR]

setkeyv(a,c('merge'))
setkeyv(b,c('merge'))

Merge_a_b=b[a,roll='nearest']

colnames(Merge_a_b)[1] <- "Mod_Z_Score_match"
colnames(Merge_a_b)[2] <- "Mod_Z_Score"

temp_z_score <- merge(temp_z_score,Merge_a_b) %>% dplyr::select(GENE,Cell_Line,Mod_Z_Score_match)
colnames(temp_z_score)[3] <- "Mod_Z_Score"

temp_z_score <- merge(temp_z_score,Mod_Z_pr_values,all.x = TRUE)

temp_z_score <- temp_z_score %>% unique() %>% dplyr::select(-Mod_Z_Score) %>% spread(Cell_Line,FDR)

rownames(temp_z_score) = temp_z_score$GENE
temp_z_score$GENE = NULL

temp_z_score <- temp_z_score[rownames(temp_hits),]
temp_z_score <- temp_z_score[,colnames(temp_hits)]

cols = colorRamp2(c(0.0, 0.10,0.20,0.30,0.40,0.50), c(tsg_green,tsg_green,"white","white","white","white"))
#cols <- colorRampPalette(c("white","#3a393b"))(n = 1000)
#cols = colorRamp2(c( 0.25, 0.5,0.75, 1), c("white","white","white","#F6CF1E"))

ha1 <- HeatmapAnnotation(foo = cbind(Type = names(cells)),annotation_name_side = "right",
                         col = col, show_legend = c("foo" = TRUE),show_annotation_name = c(foo = TRUE), # only turn off `bar`
                         height = unit(1, "cm"),name = "foo_ann")


#pdf("./paper_figs_code/fig/3-ARNT_AHR_Heatmap_common_scale.pdf",width = 10,height = 10)
Heatmap(
  as.matrix(temp_z_score),col = cols, cluster_rows = FALSE,cluster_columns = FALSE,top_annotation = ha1,
  name = "foo",show_heatmap_legend = TRUE  #Colv=NA,scale = "none", col = cols,Rowv = NA
)
#decorate_heatmap_body("foo", {grid.rect(gp = gpar(fill = "transparent", col = "black", lwd = 1))})
#dev.off()
```

```{r gator1}
picked_genes <- c("NPRL2","DEPDC5")

temp_hits <- avana_res %>% filter(GENE %in% picked_genes) %>% #filter(Cosmic_TSG == 1) %>%
  droplevels() %>% dplyr::select(GENE,Cell_Line,hit) %>% unique() %>% spread(Cell_Line,hit)
temp <- temp_hits[-1][colSums(temp_hits[-1]) > 0]
temp_hits <- temp_hits %>% dplyr::select(GENE,colnames(temp))
rownames(temp_hits) = temp_hits$GENE
temp_hits$GENE = NULL

NPRL2_Cells <- avana_res %>% filter(GENE == "NPRL2") %>% filter(hit == 1) %>% pull(Cell_Line) %>% droplevels() %>% as.vector()
DEPDC5_Cells <- avana_res %>% filter(GENE == "DEPDC5") %>% filter(hit == 1) %>% pull(Cell_Line) %>% droplevels() %>% as.vector()

Other_Cells <- avana_res %>% filter(Cell_Line %in% colnames(temp)) %>%
  filter(Cell_Line %!in% c(NPRL2_Cells,DEPDC5_Cells)) %>%
  pull(Cell_Line) %>%droplevels() %>% as.vector() %>% unique()

temp_hits <- temp_hits[unique(c(DEPDC5_Cells,NPRL2_Cells))]
order = c("DEPDC5","NPRL2")

col_order <- colSums(temp_hits) %>% sort(decreasing = TRUE)
cells <- cell_line_key %>% filter(DepMap_ID %in% names(col_order)) %>% droplevels() %>% pull(`Primary Disease`) %>% toupper()
cells <- color.bar(cells)

temp_hits <- temp_hits[match(order, rownames(temp_hits)),names(col_order)]
col = list(foo = cells)

temp_z_score <- avana_res %>% filter(GENE %in% picked_genes) %>% filter(Cell_Line %in% colnames(temp_hits)) %>%
  droplevels() %>% dplyr::select(GENE,Cell_Line,Mod_Z_Score) #%>% unique() %>% spread(Cell_Line,Mod_Z_Score)

temp_z_score$Mod_Z_Score <- round(temp_z_score$Mod_Z_Score, digits = 2) 

a=data.table(Mod_Z_Data=c(temp_z_score$Mod_Z_Score))
a[,merge:=Mod_Z_Data]

b=data.table(Mod_Z_PR=c(Mod_Z_pr_values$Mod_Z_Score))
b[,merge:=Mod_Z_PR]

setkeyv(a,c('merge'))
setkeyv(b,c('merge'))

Merge_a_b=b[a,roll='nearest']

colnames(Merge_a_b)[1] <- "Mod_Z_Score_match"
colnames(Merge_a_b)[2] <- "Mod_Z_Score"

temp_z_score <- merge(temp_z_score,Merge_a_b) %>% dplyr::select(GENE,Cell_Line,Mod_Z_Score_match)
colnames(temp_z_score)[3] <- "Mod_Z_Score"

temp_z_score <- merge(temp_z_score,Mod_Z_pr_values,all.x = TRUE)

temp_z_score <- temp_z_score %>% unique() %>% dplyr::select(-Mod_Z_Score) %>% spread(Cell_Line,FDR)

rownames(temp_z_score) = temp_z_score$GENE
temp_z_score$GENE = NULL

temp_z_score <- temp_z_score[rownames(temp_hits),]
temp_z_score <- temp_z_score[,colnames(temp_hits)]

cols = colorRamp2(c(0.0, 0.10,0.20,0.30,0.40,0.50), c(tsg_green,tsg_green,"white","white","white","white"))
#cols <- colorRampPalette(c("white","#3a393b"))(n = 1000)
#cols = colorRamp2(c( 0.25, 0.5,0.75, 1), c("white","white","white","#42616C"))

ha1 <- HeatmapAnnotation(foo = cbind(Type = names(cells)),annotation_name_side = "right",
                         col = col, show_legend = c("foo" = TRUE),show_annotation_name = c(foo = TRUE), # only turn off `bar`
                         height = unit(1, "cm"),name = "foo_ann")


#pdf("./paper_figs_code/fig/3-GATOR1_Heatmap_common_scale.pdf",width = 10,height = 10)
Heatmap(
  as.matrix(temp_z_score),col = cols, cluster_rows = FALSE,cluster_columns = FALSE,top_annotation = ha1,
  name = "foo",show_heatmap_legend = TRUE  #Colv=NA,scale = "none", col = cols,Rowv = NA
)
#decorate_heatmap_body("foo", {grid.rect(gp = gpar(fill = "transparent", col = "black", lwd = 1))})
#dev.off()
```

```{r ubiq}
picked_genes <- c("UBE2F","CUL5")

temp_hits <- avana_res %>% filter(GENE %in% picked_genes) %>% #filter(Cosmic_TSG == 1) %>%
  droplevels() %>% dplyr::select(GENE,Cell_Line,hit) %>% unique() %>% spread(Cell_Line,hit)
temp <- temp_hits[-1][colSums(temp_hits[-1]) > 0]
temp_hits <- temp_hits %>% dplyr::select(GENE,colnames(temp))
rownames(temp_hits) = temp_hits$GENE
temp_hits$GENE = NULL

CUL5_Cells <- avana_res %>% filter(GENE == "CUL5") %>% filter(hit == 1) %>% pull(Cell_Line) %>% droplevels() %>% as.vector()
UBE2F_Cells <- avana_res %>% filter(GENE == "UBE2F") %>% filter(hit == 1) %>% pull(Cell_Line) %>% droplevels() %>% as.vector()

Other_Cells <- avana_res %>% filter(Cell_Line %in% colnames(temp)) %>%
  filter(Cell_Line %!in% c(CUL5_Cells,UBE2F_Cells)) %>%
  pull(Cell_Line) %>%droplevels() %>% as.vector() %>% unique()

temp_hits <- temp_hits[unique(c(CUL5_Cells,UBE2F_Cells))]
order = c("CUL5","UBE2F")

col_order <- colSums(temp_hits) %>% sort(decreasing = TRUE)
cells <- cell_line_key %>% filter(DepMap_ID %in% names(col_order)) %>% droplevels() %>% pull(`Primary Disease`) %>% toupper()
cells <- color.bar(cells)

temp_hits <- temp_hits[match(order, rownames(temp_hits)),names(col_order)]
col = list(foo = cells)

temp_z_score <- avana_res %>% filter(GENE %in% picked_genes) %>% filter(Cell_Line %in% colnames(temp_hits)) %>%
  droplevels() %>% dplyr::select(GENE,Cell_Line,Mod_Z_Score) #%>% unique() %>% spread(Cell_Line,Mod_Z_Score)

temp_z_score$Mod_Z_Score <- round(temp_z_score$Mod_Z_Score, digits = 2) 

a=data.table(Mod_Z_Data=c(temp_z_score$Mod_Z_Score))
a[,merge:=Mod_Z_Data]

b=data.table(Mod_Z_PR=c(Mod_Z_pr_values$Mod_Z_Score))
b[,merge:=Mod_Z_PR]

setkeyv(a,c('merge'))
setkeyv(b,c('merge'))

Merge_a_b=b[a,roll='nearest']

colnames(Merge_a_b)[1] <- "Mod_Z_Score_match"
colnames(Merge_a_b)[2] <- "Mod_Z_Score"

temp_z_score <- merge(temp_z_score,Merge_a_b) %>% dplyr::select(GENE,Cell_Line,Mod_Z_Score_match)
colnames(temp_z_score)[3] <- "Mod_Z_Score"

temp_z_score <- merge(temp_z_score,Mod_Z_pr_values,all.x = TRUE)

temp_z_score <- temp_z_score %>% unique() %>% dplyr::select(-Mod_Z_Score) %>% spread(Cell_Line,FDR)

rownames(temp_z_score) = temp_z_score$GENE
temp_z_score$GENE = NULL

temp_z_score <- temp_z_score[rownames(temp_hits),]
temp_z_score <- temp_z_score[,colnames(temp_hits)]

cols = colorRamp2(c(0.0, 0.10,0.20,0.30,0.40,0.50), c(tsg_green,tsg_green,"white","white","white","white"))
#cols <- colorRampPalette(c("white","#3a393b"))(n = 1000)
#cols = colorRamp2(c( 0.25, 0.5,0.75, 1), c("white","white","white","#015050"))

ha1 <- HeatmapAnnotation(foo = cbind(Type = names(cells)),annotation_name_side = "right",
                         col = col, show_legend = c("foo" = TRUE),show_annotation_name = c(foo = TRUE), # only turn off `bar`
                         height = unit(1, "cm"),name = "foo_ann")


#pdf("./paper_figs_code/fig/3-Ubiq_ligase_Heatmap_common_scale.pdf",width = 10,height = 10)

Heatmap(
  as.matrix(temp_z_score),col = cols, cluster_rows = FALSE,cluster_columns = FALSE,top_annotation = ha1,
  name = "foo",show_heatmap_legend = TRUE, #Colv=NA,scale = "none", col = cols,Rowv = NA
)
#decorate_heatmap_body("foo", {grid.rect(gp = gpar(fill = "transparent", col = "black", lwd = 1))})
#dev.off()
```

```{r notch}
picked_genes <- c("NCSTN","PSENEN","TGFBR2")

temp_hits <- avana_res %>% filter(GENE %in% picked_genes) %>% #filter(Cosmic_TSG == 1) %>%
  droplevels() %>% dplyr::select(GENE,Cell_Line,hit) %>% unique() %>% spread(Cell_Line,hit)
temp <- temp_hits[-1][colSums(temp_hits[-1]) > 0]
temp_hits <- temp_hits %>% dplyr::select(GENE,colnames(temp))
rownames(temp_hits) = temp_hits$GENE
temp_hits$GENE = NULL

TGFBR2_Cells <- avana_res %>% filter(GENE == "TGFBR2") %>% filter(hit == 1) %>% pull(Cell_Line) %>% droplevels() %>% as.vector()
PSENEN_Cells <- avana_res %>% filter(GENE == "PSENEN") %>% filter(hit == 1) %>% pull(Cell_Line) %>% droplevels() %>% as.vector()
NCSTN_Cells <- avana_res %>% filter(GENE == "NCSTN") %>% filter(hit == 1) %>% pull(Cell_Line) %>% droplevels() %>% as.vector()

Other_Cells <- avana_res %>% filter(Cell_Line %in% colnames(temp)) %>%
  filter(Cell_Line %!in% c(PSENEN_Cells,NCSTN_Cells,TGFBR2_Cells)) %>%
  pull(Cell_Line) %>%droplevels() %>% as.vector() %>% unique()

temp_hits <- temp_hits[unique(c(PSENEN_Cells,NCSTN_Cells,TGFBR2_Cells))]
order = c("PSENEN","NCSTN","TGFBR2")

col_order <- colSums(temp_hits) %>% sort(decreasing = TRUE)
cells <- cell_line_key %>% filter(DepMap_ID %in% names(col_order)) %>% droplevels() %>% pull(`Primary Disease`) %>% toupper()
cells <- color.bar(cells)

temp_hits <- temp_hits[match(order, rownames(temp_hits)),names(col_order)]
col = list(foo = cells)

temp_z_score <- avana_res %>% filter(GENE %in% picked_genes) %>% filter(Cell_Line %in% colnames(temp_hits)) %>%
  droplevels() %>% dplyr::select(GENE,Cell_Line,Mod_Z_Score) #%>% unique() %>% spread(Cell_Line,Mod_Z_Score)

temp_z_score$Mod_Z_Score <- round(temp_z_score$Mod_Z_Score, digits = 2) 

a=data.table(Mod_Z_Data=c(temp_z_score$Mod_Z_Score))
a[,merge:=Mod_Z_Data]

b=data.table(Mod_Z_PR=c(Mod_Z_pr_values$Mod_Z_Score))
b[,merge:=Mod_Z_PR]

setkeyv(a,c('merge'))
setkeyv(b,c('merge'))

Merge_a_b=b[a,roll='nearest']

colnames(Merge_a_b)[1] <- "Mod_Z_Score_match"
colnames(Merge_a_b)[2] <- "Mod_Z_Score"

temp_z_score <- merge(temp_z_score,Merge_a_b) %>% dplyr::select(GENE,Cell_Line,Mod_Z_Score_match)
colnames(temp_z_score)[3] <- "Mod_Z_Score"

temp_z_score <- merge(temp_z_score,Mod_Z_pr_values,all.x = TRUE)

temp_z_score <- temp_z_score %>% unique() %>% dplyr::select(-Mod_Z_Score) %>% spread(Cell_Line,FDR)

rownames(temp_z_score) = temp_z_score$GENE
temp_z_score$GENE = NULL

temp_z_score <- temp_z_score[rownames(temp_hits),]
temp_z_score <- temp_z_score[,colnames(temp_hits)]

cols = colorRamp2(c(0.0, 0.10,0.20,0.30,0.40,0.50), c(tsg_green,tsg_green,"white","white","white","white"))
#cols <- colorRampPalette(c("white","#3a393b"))(n = 1000)
#cols = colorRamp2(c( 0.25, 0.5,0.75, 1), c("white","white","white","#F485D8"))

ha1 <- HeatmapAnnotation(foo = cbind(Type = names(cells)),annotation_name_side = "right",
                         col = col, show_legend = c("foo" = TRUE),show_annotation_name = c(foo = TRUE), # only turn off `bar`
                         height = unit(1, "cm"),name = "foo_ann")

#pdf("./paper_figs_code/fig/3-notch_Heatmap_common_scale.pdf",width = 10,height = 10)

Heatmap(
  as.matrix(temp_z_score),col = cols, cluster_rows = FALSE,cluster_columns = FALSE,top_annotation = ha1,
  name = "foo",show_heatmap_legend = TRUE, #Colv=NA,scale = "none", col = cols,Rowv = NA
)
#decorate_heatmap_body("foo", {grid.rect(gp = gpar(fill = "transparent", col = "black", lwd = 1))})
#dev.off()
```

```{r staga}
picked_genes <- c("MED19","TAF6L","TAF5L","TADA1","TADA2B","SUPT20H")

temp_hits <- avana_res %>% filter(GENE %in% picked_genes) %>% #filter(Cosmic_TSG == 1) %>%
  droplevels() %>% dplyr::select(GENE,Cell_Line,hit) %>% unique() %>% spread(Cell_Line,hit)
temp <- temp_hits[-1][colSums(temp_hits[-1]) > 0]
temp_hits <- temp_hits %>% dplyr::select(GENE,colnames(temp))
rownames(temp_hits) = temp_hits$GENE
temp_hits$GENE = NULL

MED19_Cells <- avana_res %>% filter(GENE == "MED19") %>% filter(hit == 1) %>% pull(Cell_Line) %>% droplevels() %>% as.vector()
TAF6L_Cells <- avana_res %>% filter(GENE == "TAF6L") %>% filter(hit == 1) %>% pull(Cell_Line) %>% droplevels() %>% as.vector()
TAF5L_Cells <- avana_res %>% filter(GENE == "TAF5L") %>% filter(hit == 1) %>% pull(Cell_Line) %>% droplevels() %>% as.vector()
TADA1_Cells <- avana_res %>% filter(GENE == "TADA1") %>% filter(hit == 1) %>% pull(Cell_Line) %>% droplevels() %>% as.vector()
TADA2B_Cells <- avana_res %>% filter(GENE == "TADA2B") %>% filter(hit == 1) %>% pull(Cell_Line) %>% droplevels() %>% as.vector()
SUPT20H_Cells <- avana_res %>% filter(GENE == "SUPT20H") %>% filter(hit == 1) %>% pull(Cell_Line) %>% droplevels() %>% as.vector()

Other_Cells <- avana_res %>% filter(Cell_Line %in% colnames(temp)) %>%
  filter(Cell_Line %!in% c(TAF5L_Cells,TADA1_Cells,TADA2B_Cells,SUPT20H_Cells,MED19_Cells,TAF6L_Cells)) %>%
  pull(Cell_Line) %>%droplevels() %>% as.vector() %>% unique()

temp_hits <- temp_hits[unique(c(TAF5L_Cells,TADA1_Cells,TADA2B_Cells,SUPT20H_Cells,MED19_Cells,TAF6L_Cells))]
order = c("TAF5L","TADA1","TADA2B","SUPT20H","MED19","TAF6L")
col_order <- colSums(temp_hits) %>% sort(decreasing = TRUE)
cells <- cell_line_key %>% filter(DepMap_ID %in% names(col_order)) %>% droplevels() %>% pull(`Primary Disease`) %>% toupper()
cells <- color.bar(cells)

temp_hits <- temp_hits[match(order, rownames(temp_hits)),names(col_order)]
col = list(foo = cells)

temp_z_score <- avana_res %>% filter(GENE %in% picked_genes) %>% filter(Cell_Line %in% colnames(temp_hits)) %>%
  droplevels() %>% dplyr::select(GENE,Cell_Line,Mod_Z_Score) #%>% unique() %>% spread(Cell_Line,Mod_Z_Score)

temp_z_score$Mod_Z_Score <- round(temp_z_score$Mod_Z_Score, digits = 2) 

a=data.table(Mod_Z_Data=c(temp_z_score$Mod_Z_Score))
a[,merge:=Mod_Z_Data]

b=data.table(Mod_Z_PR=c(Mod_Z_pr_values$Mod_Z_Score))
b[,merge:=Mod_Z_PR]

setkeyv(a,c('merge'))
setkeyv(b,c('merge'))

Merge_a_b=b[a,roll='nearest']

colnames(Merge_a_b)[1] <- "Mod_Z_Score_match"
colnames(Merge_a_b)[2] <- "Mod_Z_Score"

temp_z_score <- merge(temp_z_score,Merge_a_b) %>% dplyr::select(GENE,Cell_Line,Mod_Z_Score_match)
colnames(temp_z_score)[3] <- "Mod_Z_Score"

temp_z_score <- merge(temp_z_score,Mod_Z_pr_values,all.x = TRUE)

temp_z_score <- temp_z_score %>% unique() %>% dplyr::select(-Mod_Z_Score) %>% spread(Cell_Line,FDR)

rownames(temp_z_score) = temp_z_score$GENE
temp_z_score$GENE = NULL

temp_z_score <- temp_z_score[rownames(temp_hits),]
temp_z_score <- temp_z_score[,colnames(temp_hits)]

cols = colorRamp2(c(0.0, 0.10,0.20,0.30,0.40,0.50), c(tsg_green,tsg_green,"white","white","white","white"))
#cols <- colorRampPalette(c("white","#3a393b"))(n = 1000)
#cols = colorRamp2(c( 0.25, 0.5,0.75, 1), c("white","white","white","#DA0AEE"))

ha1 <- HeatmapAnnotation(foo = cbind(Type = names(cells)),annotation_name_side = "right",
                         col = col, show_legend = c("foo" = TRUE),show_annotation_name = c(foo = TRUE), # only turn off `bar`
                         height = unit(1, "cm"),name = "foo_ann")

#cols = c("#ffffff","#DA0AEE")

#pdf("./paper_figs_code/fig/3-staga_Heatmap_common_scale.pdf",width = 10,height = 10)
Heatmap(
  as.matrix(temp_z_score),col = cols, cluster_rows = FALSE,cluster_columns = FALSE,top_annotation = ha1,
  name = "foo",show_heatmap_legend = TRUE  #Colv=NA,scale = "none", col = cols,Rowv = NA
)
#decorate_heatmap_body("foo", {grid.rect(gp = gpar(fill = "transparent", col = "black", lwd = 1))})
#dev.off()
```

```{r fasn}
picked_genes <- c("FASN","GPAT4","CHP1","GPI","ACACA","SLC2A1","ERO1A","LSS","PGP")
temp_hits <- avana_res %>% filter(GENE %in% picked_genes) %>% #filter(Cosmic_TSG == 1) %>%
  droplevels() %>% dplyr::select(GENE,Cell_Line,hit) %>% unique() %>% spread(Cell_Line,hit)
temp <- temp_hits[-1][colSums(temp_hits[-1]) > 0]


###Code checking fisher's exact test of AML hit probabilities. 
AML <- cell_line_key %>% filter(`Subtype Disease` == "Acute Myelogenous Leukemia (AML)")
AML_tot <- avana_res %>% filter(Cell_Line %in% AML$DepMap_ID) %>% dplyr::select(Cell_Line) %>% droplevels() %>% unique() %>% nrow() #15
Other_tot <- avana_res %>% filter(Cell_Line %!in% AML$DepMap_ID) %>% dplyr::select(Cell_Line) %>% droplevels() %>% unique() %>% nrow() #548
AML_hit <- length(colnames(temp)[colnames(temp) %in% AML$DepMap_ID])
Other_hit <- length(colnames(temp)[colnames(temp) %!in% AML$DepMap_ID])
AML_table <-
matrix(c(AML_hit,AML_tot-AML_hit, Other_hit, Other_tot-Other_hit),
       nrow = 2,
       dimnames = list(PS_Hit = c("Hit", "No_Hit"),
                       AML = c("AML", "Other")))
fisher.test(AML_table)


temp_hits <- temp_hits %>% dplyr::select(GENE,colnames(temp))
rownames(temp_hits) = temp_hits$GENE
temp_hits$GENE = NULL

FASN_Cells <- avana_res %>% filter(GENE == "FASN") %>% filter(hit == 1) %>% pull(Cell_Line) %>% droplevels() %>% as.vector()
GPI_Cells <- avana_res %>% filter(GENE == "GPI") %>% filter(hit == 1) %>% pull(Cell_Line) %>% droplevels() %>% as.vector()
CHP1_Cells <- avana_res %>% filter(GENE == "CHP1") %>% filter(hit == 1) %>% pull(Cell_Line) %>% droplevels() %>% as.vector()
ACACA_Cells <- avana_res %>% filter(GENE == "ACACA") %>% filter(hit == 1) %>% pull(Cell_Line) %>% droplevels() %>% as.vector()
SLC2A1_Cells <- avana_res %>% filter(GENE == "SLC2A1") %>% filter(hit == 1) %>% pull(Cell_Line) %>% droplevels() %>% as.vector()
LSS_Cells <- avana_res %>% filter(GENE == "LSS") %>% filter(hit == 1) %>% pull(Cell_Line) %>% droplevels() %>% as.vector()
ERO1A_Cells <- avana_res %>% filter(GENE == "ERO1A") %>% filter(hit == 1) %>% pull(Cell_Line) %>% droplevels() %>% as.vector()
PGP_Cells <- avana_res %>% filter(GENE == "PGP") %>% filter(hit == 1) %>% pull(Cell_Line) %>% droplevels() %>% as.vector()
GPAT4_Cells <- avana_res %>% filter(GENE == "GPAT4") %>% filter(hit == 1) %>% pull(Cell_Line) %>% droplevels() %>% as.vector()

temp_hits <- temp_hits[unique(c(FASN_Cells,GPAT4_Cells,CHP1_Cells,GPI_Cells,ACACA_Cells,SLC2A1_Cells,ERO1A_Cells,LSS_Cells,PGP_Cells))]
order = c("FASN","GPAT4","CHP1","ACACA","GPI","SLC2A1","ERO1A","LSS","PGP")
col_order <- colSums(temp_hits) %>% sort(decreasing = TRUE)
cells <- cell_line_key %>% filter(DepMap_ID %in% names(col_order)) %>% droplevels() %>% pull(`Primary Disease`) %>% toupper()
cells <- color.bar(cells)

temp_hits <- temp_hits[match(order, rownames(temp_hits)),names(col_order)]
col = list(foo = cells)

temp_z_score <- avana_res %>% filter(GENE %in% picked_genes) %>% filter(Cell_Line %in% colnames(temp_hits)) %>%
  droplevels() %>% dplyr::select(GENE,Cell_Line,Mod_Z_Score) #%>% unique() %>% spread(Cell_Line,Mod_Z_Score)

temp_z_score$Mod_Z_Score <- round(temp_z_score$Mod_Z_Score, digits = 2) 

a=data.table(Mod_Z_Data=c(temp_z_score$Mod_Z_Score))
a[,merge:=Mod_Z_Data]

b=data.table(Mod_Z_PR=c(Mod_Z_pr_values$Mod_Z_Score))
b[,merge:=Mod_Z_PR]

setkeyv(a,c('merge'))
setkeyv(b,c('merge'))

Merge_a_b=b[a,roll='nearest']

colnames(Merge_a_b)[1] <- "Mod_Z_Score_match"
colnames(Merge_a_b)[2] <- "Mod_Z_Score"

temp_z_score <- merge(temp_z_score,Merge_a_b) %>% dplyr::select(GENE,Cell_Line,Mod_Z_Score_match)
colnames(temp_z_score)[3] <- "Mod_Z_Score"

temp_z_score <- merge(temp_z_score,Mod_Z_pr_values,all.x = TRUE)

temp_z_score <- temp_z_score %>% unique() %>% dplyr::select(-Mod_Z_Score) %>% spread(Cell_Line,FDR)

rownames(temp_z_score) = temp_z_score$GENE
temp_z_score$GENE = NULL

temp_z_score <- temp_z_score[rownames(temp_hits),]
temp_z_score <- temp_z_score[,colnames(temp_hits)]

cols = colorRamp2(c(0.0, 0.10,0.20,0.30,0.40,0.50), c(tsg_green,tsg_green,"white","white","white","white"))
#cols <- colorRampPalette(c("white","#3a393b"))(n = 1000)
#cols = colorRamp2(c( 0.25, 0.5,0.75, 1), c("white","white","white","#FF4600"))

ha1 <- HeatmapAnnotation(foo = cbind(Type = names(cells)),annotation_name_side = "right",
                         col = col, show_legend = c("foo" = TRUE),show_annotation_name = c(foo = TRUE), # only turn off `bar`
                         height = unit(1, "cm"),name = "foo_ann")


#cols = c("#ffffff","#FF4600")

#pdf("./paper_figs_code/fig/4-FASN_Heatmap_common_scale.pdf",width = 10,height = 10)
Heatmap(
  as.matrix(temp_z_score),col = cols, cluster_rows = FALSE,cluster_columns = FALSE,top_annotation = ha1,
  name = "foo",show_heatmap_legend = TRUE  #Colv=NA,scale = "none", col = cols,Rowv = NA
)
#decorate_heatmap_body("foo", {grid.rect(gp = gpar(fill = "transparent", col = "black", lwd = 1))})
#dev.off()
```

reseting workspace
```{r reset}
rm(list = ls())
if (is.integer(dev.list())) {
  dev.off()
}
cat("\014")
```