---
title: "Sanger Comparison"
output: 
  html_document:
    fig_width: 10
    fig_height: 10
---

This code was used to generate the Sanger Comparison (Supplementary Figure 3)
```{r sessioninfo}
rm(list = ls())
if (is.integer(dev.list())){dev.off()}
cat("\014")
set.seed(1)
source("functions.R")
sessionInfo()

```

```{r data_load}
cell_line_key <- read_csv("Data/DepMap-2018q4-celllines.csv")
avana_res <- read.delim("Data/avana_output_v2.txt")
Sanger_Shuffle_Corrected_FC <- read.delim("Data/Sanger_Shuffle_Corrected_FC.txt")
cell_passport <- read_csv("Data/model_list_20191104.csv") ##cell passport for sanger data
cancer_gene_census <- read_csv("Data/cancer_gene_census.csv")
NEGv1 <- read.delim("Data/NEGv1.txt")
fisher_network <- read.delim("Data/fisher_results_res_fdr_0.01_2_7_20.txt")


```

```{r data_manipulation}
oncogenes_all <- cancer_gene_census %>% filter(`Role in Cancer` %in%  c("oncogene, fusion","oncogene")) %>%
  droplevels() %>% pull(`Entrez GeneId`) %>% unique()

cosmic_tsg <- cancer_gene_census %>% 
  filter(grepl("TSG",`Role in Cancer` ))

V1 <- as.vector(as.character(Sanger_Shuffle_Corrected_FC$GENE))
entrez_IDS <- mapIds(org.Hs.eg.db, V1, 'ENTREZID', 'SYMBOL')
Sanger_Shuffle_Corrected_FC$entrez_ID = entrez_IDS

##setting up Sanger data

Sanger_Shuffle_Corrected_FC$Cosmic_TSG = 0
Sanger_Shuffle_Corrected_FC$Cosmic_TSG[Sanger_Shuffle_Corrected_FC$entrez_ID %in% cosmic_tsg$`Entrez GeneId`] = 1

cell_passport <- cell_passport %>% dplyr::select(BROAD_ID,model_id,CCLE_ID)
colnames(cell_passport) = c("Cell_Line","Sanger_ID","CCLE")
colnames(Sanger_Shuffle_Corrected_FC)[1] <- "Sanger_ID"

cell_passport <- cell_passport %>% filter(Sanger_ID %in% Sanger_Shuffle_Corrected_FC$Sanger_ID) %>% filter(!is.na(Cell_Line))
Sanger_Shuffle_Corrected_FC <- merge(Sanger_Shuffle_Corrected_FC,cell_passport)

rm(entrez_IDS)

gene_nodes = unique(c(as.character(fisher_network$g1),as.character(fisher_network$g2)))

Sanger_Shuffle_Corrected_FC$Mod_Z_Score = (Sanger_Shuffle_Corrected_FC$MEAN_FC - Sanger_Shuffle_Corrected_FC$MEAN_FC_Shuffle_Mean)/Sanger_Shuffle_Corrected_FC$SD_Shuffle_Mean

hit_gene_tab <- avana_res %>% filter(hit == 1) %>% filter(GENE %in% gene_nodes) %>% droplevels() %>% pull(GENE)
hit_gene_tab <- table(hit_gene_tab)
hit_gene_tab <- hit_gene_tab[hit_gene_tab > 1]
```

With both data set up, joining them together to compare
```{r data_join}
results_avana <- avana_res
results_sanger <- Sanger_Shuffle_Corrected_FC

results_sanger$entrezid_cell = paste(results_sanger$entrez_ID,results_sanger$Cell_Line,sep = "_")
results_avana$entrezid_cell = paste(results_avana$entrez_ID,results_avana$Cell_Line,sep = "_")

results_sanger$gene_cell = paste(results_sanger$GENE,results_sanger$Cell_Line,sep = "_")
results_avana$gene_cell = paste(results_avana$GENE,results_avana$Cell_Line,sep = "_")

results_avana_omit <- results_avana %>% filter(entrezid_cell %in% results_sanger$entrezid_cell) %>% filter(!is.na(entrez_ID))
results_sanger_omit <- results_sanger %>% filter(entrezid_cell %in% results_avana$entrezid_cell) %>% filter(!is.na(entrez_ID))

results_avana_omit <- results_avana_omit %>% dplyr::select(GENE,Cell_Line,MEAN_FC,percentage,Mod_Z_Score,MEAN_FC_Shuffle_Mean,SD_Shuffle_Mean,entrez_ID,entrezid_cell,hit)
results_sanger_omit <- results_sanger_omit %>% dplyr::select(GENE,Cell_Line,MEAN_FC,percentage,Mod_Z_Score,MEAN_FC_Shuffle_Mean,SD_Shuffle_Mean,entrez_ID,entrezid_cell,Cosmic_TSG)

colnames(results_avana_omit) = c("GENE_Avana","Cell_Line","Avana_MEAN_FC","Avana_percentage","Avana_Mod_Z_Score",
                                 "Avana_MEAN_FC_Shuffle_Mean","Avana_SD_Shuffle_Mean",
                                 "Avana_entrez_ID","entrezid_cell","hit")

colnames(results_sanger_omit) = c("GENE_Sanger","Cell_Line","Sanger_MEAN_FC","Sanger_percentage","Sanger_Mod_Z_Score",
                                  "Sanger_MEAN_FC_Shuffle_Mean","Sanger_SD_Shuffle_Mean",
                                  "Sanger_entrez_ID","entrezid_cell","Cosmic_TSG")

comparison_Max <- merge(results_avana_omit,results_sanger_omit)

comparison_Max$`Avana Status` = "Not a hit"
comparison_Max$`Avana Status`[comparison_Max$hit == 1 & comparison_Max$GENE_Avana %in% names(hit_gene_tab)] = "Frequent Hit"

```

Supplementary Figure 3b
```{r plot_3b}
p <- comparison_Max %>% filter(`Avana Status` == "Frequent Hit") %>%
  ggplot(aes(x = Sanger_Mod_Z_Score,y = Avana_Mod_Z_Score)) + geom_vline(xintercept = 0, color = "red") + ylim(0,max(comparison_Max$Avana_Mod_Z_Score)) +
  geom_point() + theme_Publication() + xlab("Sanger Mod Z-Score") + ylab("Avana Mod Z-Score") + ggtitle("Avana Frequent Hits in Sanger") + geom_abline() 
p1 <- ggExtra::ggMarginal(p, type = "histogram", margins = "x", size = 4)

p1

```

Alternative plot showing that the density is shifted
```{r plot_3b_alt}
p2 <- comparison_Max %>% ggplot(aes(Sanger_Mod_Z_Score,fill = `Avana Status`)) + geom_density(alpha = 0.5) + theme_Publication() +
  scale_fill_manual(values=c("#13d4c0","#999999"))  + xlab("Sanger Modified Z-Score") + ylab("Density") + ggtitle("Avana Frequent Hits in Sanger")

p2

```

PR Curve for Sanger and Avana. TP = TSGs, FP = Onco, recall in this instance is defined as the number of hits observed.
Filtered for cell lines selected in both sets. Code is analogous to code used to generate PR curve observed in figure 1.
```{r PR_Curve}
comparison_Max$NEG = 0
comparison_Max$NEG[comparison_Max$Avana_entrez_ID %in% NEGv1$ENTREZ_ID] = 1

oncogenes_scores <- comparison_Max %>% filter(Avana_entrez_ID %in% oncogenes_all) %>% droplevels() %>% pull(Avana_Mod_Z_Score)
NEG_scores <- comparison_Max %>% filter(NEG == 1) %>% droplevels() %>% pull(Avana_Mod_Z_Score)
tsg_scores <- comparison_Max %>% filter(Cosmic_TSG == 1) %>% droplevels() %>% pull(Avana_Mod_Z_Score)
FP = c(oncogenes_scores,NEG_scores)
pr_mod_Z_avana <-pr.curve(scores.class0 = tsg_scores , scores.class1 = FP, curve = TRUE)
pr_mod_Z_avana_dat <- data.frame(Recall = pr_mod_Z_avana$curve[,1],Precision = pr_mod_Z_avana$curve[,2],Score = pr_mod_Z_avana$curve[,3])
pr_mod_Z_avana_dat $Precision = round(pr_mod_Z_avana_dat$Precision,digits = 2)
pr_mod_Z_avana_dat$Recall = round(pr_mod_Z_avana_dat$Recall,digits = 2)
pr_mod_Z_avana_dat$Score = round(pr_mod_Z_avana_dat$Score,digits = 2)
pr_mod_Z_avana_dat <- pr_mod_Z_avana_dat %>% unique()

observation_count <- sapply(pr_mod_Z_avana_dat$Score, function(x) length(tsg_scores[tsg_scores > x]))
pr_mod_Z_avana_dat$count <- observation_count
pr_mod_Z_avana_dat <- pr_mod_Z_avana_dat %>% arrange(count)

oncogenes_scores <- comparison_Max %>% filter(Avana_entrez_ID %in% oncogenes_all) %>% droplevels() %>% pull(Sanger_Mod_Z_Score)
NEG_scores <- comparison_Max %>% filter(NEG == 1) %>% droplevels() %>% pull(Sanger_Mod_Z_Score)
tsg_scores <- comparison_Max %>% filter(Cosmic_TSG == 1) %>% droplevels() %>% pull(Sanger_Mod_Z_Score)
FP = c(oncogenes_scores,NEG_scores)
pr_mod_Z_sanger <-pr.curve(scores.class0 = tsg_scores , scores.class1 = FP, curve = TRUE)
pr_mod_Z_sanger_dat <- data.frame(Recall = pr_mod_Z_sanger$curve[,1],Precision = pr_mod_Z_sanger$curve[,2],Score = pr_mod_Z_sanger$curve[,3])
pr_mod_Z_sanger_dat $Precision = round(pr_mod_Z_sanger_dat$Precision,digits = 2)
pr_mod_Z_sanger_dat$Recall = round(pr_mod_Z_sanger_dat$Recall,digits = 2)
pr_mod_Z_sanger_dat$Score = round(pr_mod_Z_sanger_dat$Score,digits = 2)
pr_mod_Z_sanger_dat <- pr_mod_Z_sanger_dat %>% unique()

observation_count <- sapply(pr_mod_Z_sanger_dat$Score, function(x) length(tsg_scores[tsg_scores > x]))
pr_mod_Z_sanger_dat$count <- observation_count
pr_mod_Z_sanger_dat <- pr_mod_Z_sanger_dat %>% arrange(count)

pr_mod_Z_sanger_dat <- as.data.table(pr_mod_Z_sanger_dat)
pr_mod_Z_sanger_dat_plot <- as.data.frame(pr_mod_Z_sanger_dat[,.SD[which.max(count)],by=Precision]) %>% fix_count()
pr_mod_Z_avana_dat <- as.data.table(pr_mod_Z_avana_dat)
pr_mod_Z_avana_dat_plot <- as.data.frame(pr_mod_Z_avana_dat[,.SD[which.max(count)],by=Precision]) %>% fix_count()

ggplot() + ylim(c(0.8,1)) + xlim(c(0,250)) + theme_Publication() + ylab("Precision") + xlab("Count") +
  geom_line(aes(y = pr_mod_Z_avana_dat_plot$Precision, x = pr_mod_Z_avana_dat_plot$count, color = "Avana"),alpha = 0.8,color="red") +
  geom_line(aes(y = pr_mod_Z_sanger_dat_plot$Precision, x = pr_mod_Z_sanger_dat_plot$count, color = "Sanger"),alpha = 0.8,color="black") +
  theme(legend.position="right") +
  geom_hline(yintercept = 0.9,color="black", linetype= 3)

```